---
title: "CNP_Analysis_PartTwo"
author: "Katelynn"
date: "2024-05-30"
output: html_document
---
This is second analysis for this manuscript following the resubmission. Since the first script, I switched to primarily using Rmarkdown for my analyses, with a second figure rendering document. 

#Load Libraries
```{r}
library(tidyverse)
library(rLakeAnalyzer)
library(lubridate)
library(readxl)
require(grid) 
library(strucchange)
library(broom)
library(patchwork)
library(plotrix)
library(dataRetrieval)
library(ggtext)
library(ggforce)
library(vegan)
library(ggrepel)
library(BiodiversityR)
library(cimir)
library(ggpubr)
library(factoextra)

```

I found it helpful in my second manuscript to start my analysis in an R markdown file so I can easily comment and write out findings underneath each figure that I am making, so I am taking the same approach with this analysis. 

***Update: I am currently switching my ANOVAs to Kruskal-Wallis tests with Dunn Post-hoc tests for non-parametric data.


Reworking the analysis: 
1. Physical Properties of the Lake
2. Biological Factors - Phytos and Toxins and Seston and Nutrients. 
3. Multivariate Analyses for Drivers of the Bloom. 


## 1. Physical Properties of the Lake. 


### Missisquoi Bay

#### Temperature

```{r}
MB_Profiler <- read_csv("./Clean Data/MB_Profiler_2021_Clean.csv") %>%
  filter(Month >= 6 & Month < 11) %>%
  mutate(Date = make_date(Year, Month, Day)) %>%
  mutate(Group = if_else(Date >= as.Date("2021-06-15") & Date <= as.Date("2021-06-23"), 1, 0),
         Group = if_else(Date == as.Date("2021-06-25"), 2, Group),
         Group = if_else(Date >= as.Date("2021-06-28") & Date <= as.Date("2021-07-03"), 3, Group),
         Group = if_else(Date >= as.Date("2021-07-06") & Date <= as.Date("2021-07-15"), 4, Group),
         Group = if_else(Date >= as.Date("2021-07-17") & Date <= as.Date("2021-08-21"), 5, Group),
         Group = if_else(Date >= as.Date("2021-08-23") & Date <= as.Date("2021-09-04"), 6, Group),
         Group = if_else(Date >= as.Date("2021-09-06") & Date <= as.Date("2021-09-08"), 7, Group),
         Group = if_else(Date >= as.Date("2021-09-10") & Date <= as.Date("2021-10-01"), 8, Group),
         Group = if_else(Date >= as.Date("2021-10-03") & Date <= as.Date("2021-10-05"), 9, Group),
         Group = if_else(Date >= as.Date("2021-10-07") & Date <= as.Date("2021-10-15"), 10, Group),
         Group = if_else(Date >= as.Date("2021-10-18") & Date <= as.Date("2021-10-22"), 11, Group),
         Group = if_else(Date >= as.Date("2021-10-24") & Date <= as.Date("2021-10-25"), 12, Group),
         Group = if_else(Date >= as.Date("2021-10-27") & Date <= as.Date("2021-10-31"), 13, Group)) %>%
  select(-Date, -Remove)



MB_Temp <- MB_Profiler %>%
  select(Depth, datetime, Temp_C, Month, Day, Year, Group) %>%
  filter(Depth == 1.0 | Depth == 2.5) %>%
  group_by(Depth, datetime, Group) %>%
  summarize(Temp_C = mean(Temp_C)) %>%
  mutate(Depth = as.character(Depth)) %>%
  ggplot(aes(x=datetime, y=Temp_C, color=Depth, group=Group)) +
       annotate("rect", xmin = as_datetime("2021-06-01 00:00:00"), xmax = as_datetime("2021-08-07 00:00:00"), ymin = 0, ymax = 30,
           fill = "grey91") +
  annotate("rect", xmin = as_datetime("2021-08-07 00:00:00"), xmax = as_datetime("2021-08-12 00:00:00"), ymin = 0, ymax =30,
           fill = "grey98") +
  annotate("rect", xmin = as_datetime("2021-08-12 00:00:00"), xmax = as_datetime("2021-08-20 00:00:00"), ymin = 0, ymax =30,
           fill = "grey91") +
  annotate("rect", xmin = as_datetime("2021-08-20 00:00:00"), xmax = as_datetime("2021-08-24 00:00:00"), ymin = 0, ymax =30,
           fill = "grey98") +
    annotate("rect", xmin = as_datetime("2021-08-24 00:00:00"), xmax = as_datetime("2021-09-03 00:00:00"), ymin = 0, ymax =30,
           fill = "grey91") +
    annotate("rect", xmin = as_datetime("2021-09-03 00:00:00"), xmax = as_datetime("2021-09-15 00:00:00"), ymin = 0, ymax =30,
           fill = "grey98") +
    annotate("rect", xmin = as_datetime("2021-09-15 00:00:00"), xmax = as_datetime("2021-09-27 00:00:00"), ymin = 0, ymax =30,
           fill = "grey91") +
    annotate("rect", xmin = as_datetime("2021-09-27 00:00:00"), xmax = as_datetime("2021-10-31 00:00:00"), ymin = 0, ymax =30,
           fill = "grey98") +
   annotate(geom="text", x= as_datetime("2021-06-05 00:00:00"), y=31, label="PrB",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-08-09 12:00:00"), y=29, label="E1",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-08-15 00:00:00"), y=31, label="PB1",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-08-22 00:00:00"), y=29, label="BC1",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-08-28 00:00:00"), y=31, label="E2",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-09-07 00:00:00"), y=29, label="PB2",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-09-18 00:00:00"), y=31, label="BC2",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-09-30 12:00:00"), y=29, label="PoB",
           color="black", size=1.4) +
  geom_line(size = 0.5) + 
  scale_color_manual(values=c("orangered3", "dodgerblue3"))+
  theme_classic() +
  ggtitle("A")+
  ylab("Water Temperature (C)")+
  xlab("") +
   theme(axis.title = element_text(size=8), axis.text=element_text(size=7),
        legend.title = element_text(size = 8), 
        legend.key.size = unit(0.5, 'cm'), legend.text = element_text(size=7), legend.position = "none",
        plot.title = element_text(size=9),
        plot.margin = unit(c(0, 0, 0, 0.1), 
                           "cm"))

```

```{r}

MB_DO <- MB_Profiler %>%
  select(Depth, datetime, ODOmgL, Month, Day, Year, Group) %>%
  filter(Depth == 1.0 | Depth == 2.5) %>%
  group_by(Depth, datetime, Group) %>%
  summarize(DO = mean(ODOmgL)) %>%
  mutate(Depth = as.character(Depth)) %>%
  ggplot(aes(x=datetime, y=DO, color=Depth, group=Group)) +
       annotate("rect", xmin = as_datetime("2021-06-01 00:00:00"), xmax = as_datetime("2021-08-07 00:00:00"), ymin = 0, ymax = 20,
           fill = "grey91") +
  annotate("rect", xmin = as_datetime("2021-08-07 00:00:00"), xmax = as_datetime("2021-08-12 00:00:00"), ymin = 0, ymax =20,
           fill = "grey98") +
  annotate("rect", xmin = as_datetime("2021-08-12 00:00:00"), xmax = as_datetime("2021-08-20 00:00:00"), ymin = 0, ymax =20,
           fill = "grey91") +
  annotate("rect", xmin = as_datetime("2021-08-20 00:00:00"), xmax = as_datetime("2021-08-24 00:00:00"), ymin = 0, ymax =20,
           fill = "grey98") +
    annotate("rect", xmin = as_datetime("2021-08-24 00:00:00"), xmax = as_datetime("2021-09-03 00:00:00"), ymin = 0, ymax =20,
           fill = "grey91") +
    annotate("rect", xmin = as_datetime("2021-09-03 00:00:00"), xmax = as_datetime("2021-09-15 00:00:00"), ymin = 0, ymax =20,
           fill = "grey98") +
    annotate("rect", xmin = as_datetime("2021-09-15 00:00:00"), xmax = as_datetime("2021-09-27 00:00:00"), ymin = 0, ymax =20,
           fill = "grey91") +
    annotate("rect", xmin = as_datetime("2021-09-27 00:00:00"), xmax = as_datetime("2021-10-31 00:00:00"), ymin = 0, ymax =20,
           fill = "grey98") +
   annotate(geom="text", x= as_datetime("2021-06-05 00:00:00"), y=20.6, label="PrB",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-08-09 12:00:00"), y=19.4, label="E1",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-08-15 00:00:00"), y=20.6, label="PB1",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-08-22 00:00:00"), y=19.4, label="BC1",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-08-28 00:00:00"), y=20.6, label="E2",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-09-07 00:00:00"), y=19.4, label="PB2",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-09-18 00:00:00"), y=20.6, label="BC2",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-09-30 12:00:00"), y=19.4, label="PoB",
           color="black", size=1.4) +
  geom_line(size = 0.5) + 
  scale_color_manual(values=c("orangered3", "dodgerblue3"))+
  theme_classic() +
  ggtitle("C")+
  ylab("Dissolved Oxygen (mg/L)")+
  xlab("") +
   theme(axis.title = element_text(size=8), axis.text=element_text(size=7),
        legend.title = element_text(size = 8), 
        legend.key.size = unit(0.5, 'cm'), legend.text = element_text(size=7), legend.position = "none",
        plot.title = element_text(size=9),
        plot.margin = unit(c(0, 0, 0, 0.1), 
                           "cm"))
```


#### Stability

```{r}
MB_bathy <- approx.bathy(Zmax = 5.0, lkeArea= 78000000, Zmean = 2.8, method = "voldev", zinterval = 0.5) #Approximates bathymetry (Cone or Voldev)

names(MB_bathy)[2] <- "areas" #Needs this column name to work with rlakeanalyzer

MB_Schmidt <- MB_Profiler %>%
  select(Depth, datetime, Temp_C, Month, Day, Year, Group) %>%
  group_by(Depth, datetime, Month, Day, Year, Group) %>%
  summarize(Temp_C = mean(Temp_C)) %>%
  group_by(datetime, Group) %>%
  mutate(SS = schmidt.stability(wtr = Temp_C, depths = Depth, bthA = MB_bathy$areas, bthD = MB_bathy$depths)) %>%
  select(datetime, SS, Group) %>%
  unique()

MB_SS <- MB_Schmidt %>%
  filter(SS > -100) %>%
  ggplot(aes(x=datetime, y=SS, group=Group)) +
     annotate("rect", xmin = as_datetime("2021-06-01 00:00:00"), xmax = as_datetime("2021-08-07 00:00:00"), ymin = 0, ymax = 20,
           fill = "grey91") +
  annotate("rect", xmin = as_datetime("2021-08-07 00:00:00"), xmax = as_datetime("2021-08-12 00:00:00"), ymin = 0, ymax =20,
           fill = "grey98") +
  annotate("rect", xmin = as_datetime("2021-08-12 00:00:00"), xmax = as_datetime("2021-08-20 00:00:00"), ymin = 0, ymax =20,
           fill = "grey91") +
  annotate("rect", xmin = as_datetime("2021-08-20 00:00:00"), xmax = as_datetime("2021-08-24 00:00:00"), ymin = 0, ymax =20,
           fill = "grey98") +
    annotate("rect", xmin = as_datetime("2021-08-24 00:00:00"), xmax = as_datetime("2021-09-03 00:00:00"), ymin = 0, ymax =20,
           fill = "grey91") +
    annotate("rect", xmin = as_datetime("2021-09-03 00:00:00"), xmax = as_datetime("2021-09-15 00:00:00"), ymin = 0, ymax =20,
           fill = "grey98") +
    annotate("rect", xmin = as_datetime("2021-09-15 00:00:00"), xmax = as_datetime("2021-09-27 00:00:00"), ymin = 0, ymax =20,
           fill = "grey91") +
    annotate("rect", xmin = as_datetime("2021-09-27 00:00:00"), xmax = as_datetime("2021-10-31 00:00:00"), ymin = 0, ymax =20,
           fill = "grey98") +
   annotate(geom="text", x= as_datetime("2021-06-05 00:00:00"), y=20.6, label="PrB",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-08-09 12:00:00"), y=19.4, label="E1",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-08-15 00:00:00"), y=20.6, label="PB1",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-08-22 00:00:00"), y=19.4, label="BC1",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-08-28 00:00:00"), y=20.6, label="E2",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-09-07 00:00:00"), y=19.4, label="PB2",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-09-18 00:00:00"), y=20.6, label="BC2",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-09-30 12:00:00"), y=19.4, label="PoB",
           color="black", size=1.4) +
  geom_line()+
  theme_classic()+ 
  ylab(bquote('Schmidt Stability (J/m'^2~")")) +
  xlab("")+
  ggtitle("E")+
  ylim(0,21)+
    theme(axis.title = element_text(size=8), axis.text=element_text(size=7),
        legend.title = element_text(size = 8), 
        legend.key.size = unit(0.5, 'cm'), legend.text = element_text(size=7),
        plot.title = element_text(size=9),
        plot.margin = unit(c(0, 0, 0, 0.1), 
                           "cm"))
  
```

#### Stream Gauge Flow
```{r}
Precip_Data_MR <- importRDB1("https://nwis.waterservices.usgs.gov/nwis/iv/?sites=04294000&parameterCd=00060&startDT=2017-06-01T00:00:00.000-04:00&endDT=2021-10-31T23:59:59.999-04:00&siteStatus=all&format=rdb") %>%
  mutate(Year = year(datetime),
         Month = month(datetime),
         Day = day(datetime)) %>%
  group_by(Day, Month, Year) %>%
  summarise(Avg_SF = mean(X67399_00060)) %>%
  mutate(Date = make_date(Year, Month, Day)) %>%
  filter(Month >= 6 & Month <= 11 & Year == 2021)


Precip_Data_RR <- importRDB1("https://nwis.waterservices.usgs.gov/nwis/iv/?sites=04294140&parameterCd=00060&startDT=2017-06-01T00:00:00.000-04:00&endDT=2021-10-31T23:59:59.999-04:00&siteStatus=all&format=rdb") %>%
  mutate(Year = year(datetime),
         Month = month(datetime),
         Day = day(datetime)) %>%
  group_by(Day, Month, Year) %>%
  summarise(Avg_SF = mean(X67402_00060)) %>%
  mutate(Date = make_date(Year, Month, Day)) %>%
  filter(Month >= 6 & Month <= 11 & Year == 2021)


Precip_Data_MB <- full_join(Precip_Data_RR, Precip_Data_MR) %>%
  group_by(Day, Month, Year, Date) %>%
  summarise(Sum_SF = sum(Avg_SF))


MB_SF <- Precip_Data_MB %>%
  ggplot(aes(x=Date, y=Sum_SF))+
   annotate("rect", xmin = as.Date("2021-06-01"), xmax = as.Date("2021-08-07"), ymin = 0, ymax = 2500,
           fill = "grey91") +
  annotate("rect", xmin = as.Date("2021-08-07"), xmax = as.Date("2021-08-12"), ymin = 0, ymax =2500,
           fill = "grey98") +
  annotate("rect", xmin = as.Date("2021-08-12"), xmax = as.Date("2021-08-20"), ymin = 0, ymax = 2500,
           fill = "grey91") +
  annotate("rect", xmin = as.Date("2021-08-20"), xmax = as.Date("2021-08-24"), ymin = 0, ymax = 2500,
           fill = "grey98") +
    annotate("rect", xmin = as.Date("2021-08-24"), xmax = as.Date("2021-09-03"), ymin = 0, ymax = 2500,
           fill = "grey91") +
    annotate("rect", xmin = as.Date("2021-09-03"), xmax = as.Date("2021-09-15"), ymin = 0, ymax = 2500,
           fill = "grey98") +
    annotate("rect", xmin = as.Date("2021-09-15"), xmax = as.Date("2021-09-27"), ymin = 0, ymax = 2500,
           fill = "grey91") +
    annotate("rect", xmin = as.Date("2021-09-27"), xmax = as.Date("2021-10-31"), ymin = 0, ymax = 2500,
           fill = "grey98") +
  annotate(geom="text", x= as.Date("2021-06-05"), y=2575, label="PrB",
           color="black", size=1.4) +
  annotate(geom="text", x= as.Date("2021-08-10"), y=2425, label="E1",
           color="black", size=1.4) +
  annotate(geom="text", x= as.Date("2021-08-15"), y=2575, label="PB1",
           color="black", size=1.4) +
  annotate(geom="text", x= as.Date("2021-08-22"), y=2425, label="BC1",
           color="black", size=1.4) +
  annotate(geom="text", x= as.Date("2021-08-28"), y=2575, label="E2",
           color="black", size=1.4) +
  annotate(geom="text", x= as.Date("2021-09-07"), y=2425, label="PB2",
           color="black", size=1.4) +
  annotate(geom="text", x= as.Date("2021-09-18"), y=2575, label="BC2",
           color="black", size=1.4) +
  annotate(geom="text", x= as.Date("2021-10-01"), y=2425, label="PoB",
           color="black", size=1.4) +
  geom_line(linewidth=1)+
  theme_classic()+ 
  ylab(bquote('Stream Gauge Flow (ft'^3~"/s)")) +
  xlab("") +
  ggtitle("I")+
   theme(axis.title = element_text(size=8), axis.text=element_text(size=7),
        legend.title = element_text(size = 8), 
        legend.key.size = unit(0.5, 'cm'), legend.text = element_text(size=7),
        plot.title = element_text(size=9),
        plot.margin = unit(c(0, 0, 0, 0.1), 
                           "cm"))


## Identifying rain event in late June that delivered LOTs OF NUTRIENTS. 
precip_MB <- Precip_Data_MB %>%
  mutate(month = month(Date)) %>%
  filter(month == 8) #%>%
  ggplot(aes(x=Date, y=Sum_SF))+
   geom_line(linewidth=1)+
  theme_classic()
  

```


#### Wind Speed and Direction
```{r}
MB_Met <- read_csv("./Clean Data/MB_Met_Clean.csv") %>%
  select(Year, Month, Day, Datetime, Wind_Direction, Wind_Speed, Temperature, PAR, Temp1) %>%
  filter(Year == 2021) %>%
  mutate(Date = make_date(Year, Month, Day)) %>%
  mutate(Group = if_else(Date < as.Date("2021-09-30"), 1, 0),
         Group = if_else(Date >= as.Date("2021-10-11"), 2, Group)) %>%
  filter(Group != 0)

library(ggformula)

MB21Wind <- MB_Met %>%
  filter(Month>=6 & Month < 11) %>%
  filter(Year == 2021) %>%
  ggplot(aes(x=Datetime, y=Wind_Speed, group=Group)) +
   annotate("rect", xmin = as_datetime("2021-06-01 00:00:00"), xmax = as_datetime("2021-08-07 00:00:00"), ymin = 0, ymax = 10,
           fill = "grey91") +
  annotate("rect", xmin = as_datetime("2021-08-07 00:00:00"), xmax = as_datetime("2021-08-12 00:00:00"), ymin = 0, ymax =10,
           fill = "grey98") +
  annotate("rect", xmin = as_datetime("2021-08-12 00:00:00"), xmax = as_datetime("2021-08-20 00:00:00"), ymin = 0, ymax =10,
           fill = "grey91") +
  annotate("rect", xmin = as_datetime("2021-08-20 00:00:00"), xmax = as_datetime("2021-08-24 00:00:00"), ymin = 0, ymax =10,
           fill = "grey98") +
    annotate("rect", xmin = as_datetime("2021-08-24 00:00:00"), xmax = as_datetime("2021-09-03 00:00:00"), ymin = 0, ymax =10,
           fill = "grey91") +
    annotate("rect", xmin = as_datetime("2021-09-03 00:00:00"), xmax = as_datetime("2021-09-15 00:00:00"), ymin = 0, ymax =10,
           fill = "grey98") +
    annotate("rect", xmin = as_datetime("2021-09-15 00:00:00"), xmax = as_datetime("2021-09-27 00:00:00"), ymin = 0, ymax =10,
           fill = "grey91") +
    annotate("rect", xmin = as_datetime("2021-09-27 00:00:00"), xmax = as_datetime("2021-10-31 00:00:00"), ymin = 0, ymax =10,
           fill = "grey98") +
  annotate(geom="text", x= as_datetime("2021-06-05 00:00:00"), y=10.25, label="PrB",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-08-09 12:00:00"), y=9.75, label="E1",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-08-15 00:00:00"), y=10.25, label="PB1",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-08-22 00:00:00"), y=9.75, label="BC1",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-08-28 00:00:00"), y=10.25, label="E2",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-09-07 00:00:00"), y=9.75, label="PB2",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-09-18 00:00:00"), y=10.25, label="BC2",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-09-30 12:00:00"), y=9.75, label="PoB",
           color="black", size=1.4) +
  geom_spline(linewidth=0.5) +
  theme_classic() +
  ggtitle("G") +
  ylab("Wind Speed (m/s)") +
  ylim(0,10.5) +
  xlab("") +
  #scale_x_date(breaks=pretty_breaks(n=6)) +
  theme(axis.title = element_text(size=8), axis.text=element_text(size=7),
        legend.title = element_text(size = 8),
        legend.key.size = unit(0.5, 'cm'), legend.text = element_text(size=7),
        plot.title = element_text(size=9),
        plot.margin = unit(c(0, 0, 0, 0.1), 
                           "cm"))


MB_WindDir <- MB_Met %>%
  filter(Wind_Direction >= 0) %>%
  filter(Month>=6 & Month < 11) %>%
  filter(Year == 2021) %>%
  ggplot(aes(x=Datetime, y=Wind_Direction)) +
  geom_spline(linewidth=0.5) +
  theme_classic() +
  ggtitle("E") +
  ylab("Wind Direction") +
  xlab("") +
  #scale_x_date(breaks=pretty_breaks(n=6)) +
  theme(plot.title = element_text(hjust = 0, size=7), axis.title = element_text(size=7), axis.text=element_text(size=6),
        legend.title = element_text(size = 5), 
        legend.key.size = unit(0.07, 'in'), legend.text = element_text(size=3.8))
```

#### Air Temperature
```{r}
MB_AirTemp <- MB_Met %>%
  filter(Month>=6 & Month < 11) %>%
  filter(Year == 2021) %>%
  ggplot(aes(x=Datetime, y=Temp1)) +
  geom_spline(linewidth=0.5) +
  theme_classic() +
  ggtitle("F") +
  ylab("Air Temperature (C)") +
  xlab("") +
  #scale_x_date(breaks=pretty_breaks(n=6)) +
  theme(plot.title = element_text(hjust = 0, size=7), axis.title = element_text(size=7), axis.text=element_text(size=6),
        legend.title = element_text(size = 5), 
        legend.key.size = unit(0.07, 'in'), legend.text = element_text(size=3.8))

```

#### PAR
```{r}
MB_PAR <- MB_Met %>%
  filter(PAR >= 0) %>%
  filter(Month>=6 & Month < 11) %>%
  filter(Year == 2021) %>%
  ggplot(aes(x=Datetime, y=PAR)) +
  geom_line(linewidth=0.25) +
  theme_classic() +
  ggtitle("G") +
  ylab("PAR") +
  xlab("Date") +
  xlim(as.POSIXct("2021-06-01 00:00:00"), as.POSIXct("2021-10-31 23:59:59")) +
  #scale_x_date(breaks=pretty_breaks(n=6)) +
  theme(plot.title = element_text(hjust = 0, size=7), axis.title = element_text(size=7), axis.text=element_text(size=6),
        legend.title = element_text(size = 5), 
        legend.key.size = unit(0.07, 'in'), legend.text = element_text(size=3.8))

```

#### pH
```{r}
MB_pH <- MB_Profiler %>%
  select(Depth, datetime, pH, Month, Day, Year) %>%
  filter(Month >= 6 & Month < 11) %>%
  ggplot(aes(x=datetime, y=pH)) + 
  geom_spline(size = 1) + 
  theme_classic() +
  ggtitle("H")+
  ylab("pH")+
  xlab("") +
  theme(plot.title = element_text(hjust = 0, size=7), axis.title = element_text(size=7), axis.text=element_text(size=6),
        legend.title = element_text(size = 5), 
        legend.key.size = unit(0.07, 'in'), legend.text = element_text(size=3.8))

```

#### DOM Flourescence. 
```{r}

MB_DOM <- MB_Profiler %>%
  select(Depth, datetime, fDOM_RFU, Month, Day, Year) %>%
  filter(Month >= 6 & Month < 11) %>%
  ggplot(aes(x=datetime, y=fDOM_RFU)) + 
  geom_spline(size = 1.00) + 
  scale_color_manual(values=c("orangered3", "cadetblue4"))+
  theme_classic() +
  ggtitle("A")+
  ylab("Flourescent DOM (RFU)")+
  xlab("") +
  theme(plot.title = element_text(hjust = 0, size=7), axis.title = element_text(size=7), axis.text=element_text(size=6),
        legend.title = element_text(size = 5), 
        legend.key.size = unit(0.07, 'in'), legend.text = element_text(size=3.8))
```
Make these publication plots in a separate R script. 



## Nutrient Plots: 

```{r}

### Load Data

Nut_Fig_Data <- All_Combined %>%
  select(-Anatoxin, -Microcystin)


## Missisquoi Bay


# Phosphorus

MB_P <- Nut_Fig_Data %>%
  filter(Station == "MB") %>%
  select(Location, Date, Water_TP_mgL) %>%
  mutate(Water_TP_ugL = Water_TP_mgL * 1000) %>%
  group_by(Location, Date) %>%
  summarize(Water_TP_ugL = mean(Water_TP_ugL)) %>%
  pivot_wider(names_from="Location", values_from = "Water_TP_ugL") %>%
  select(-IWC) %>%
  na.omit()

MB_SesP <- Nut_Fig_Data %>%
  select(SestonP_ugL, Date, Station) %>%
  filter(Station == "MB") %>%
  na.omit() %>%
  group_by(Date) %>%
  dplyr::summarize(SestonP_ugL = mean(SestonP_ugL))

MB_P <- full_join(MB_P, MB_SesP, by=c("Date")) %>%
  pivot_longer(cols=c("SestonP_ugL", "bottom", "surface"), names_to = "Location", values_to = "TP_ugL") %>%
  mutate(Location = if_else(Location == "bottom", "Water TP - 2.5m", Location),
         Location = if_else(Location == "surface", "Water TP - 0.5m", Location),
         Location = if_else(Location == "SestonP_ugL", "Seston TP - IWC", Location))

MB_P_Fig <- MB_P %>%
  mutate(Date=as.Date(Date))%>%
  filter(Date > as.Date("2021-06-01") & Date <= as.Date("2021-11-01")) %>%
  ggplot() + 
  annotate("rect", xmin = as.Date("2021-06-01"), xmax = as.Date("2021-08-07"), ymin = 0, ymax = 200,
           fill = "grey91") +
  annotate("rect", xmin = as.Date("2021-08-07"), xmax = as.Date("2021-08-12"), ymin = 0, ymax =200,
           fill = "grey98") +
  annotate("rect", xmin = as.Date("2021-08-12"), xmax = as.Date("2021-08-20"), ymin = 0, ymax = 200,
           fill = "grey91") +
  annotate("rect", xmin = as.Date("2021-08-20"), xmax = as.Date("2021-08-24"), ymin = 0, ymax = 200,
           fill = "grey98") +
    annotate("rect", xmin = as.Date("2021-08-24"), xmax = as.Date("2021-09-03"), ymin = 0, ymax = 200,
           fill = "grey91") +
    annotate("rect", xmin = as.Date("2021-09-03"), xmax = as.Date("2021-09-15"), ymin = 0, ymax = 200,
           fill = "grey98") +
    annotate("rect", xmin = as.Date("2021-09-15"), xmax = as.Date("2021-09-27"), ymin = 0, ymax = 200,
           fill = "grey91") +
    annotate("rect", xmin = as.Date("2021-09-27"), xmax = as.Date("2021-10-31"), ymin = 0, ymax = 200,
           fill = "grey98") +
  geom_line(aes(x = Date, y = TP_ugL, color=Location), size = 0.75) + 
  geom_point(aes(x=Date, y=TP_ugL, shape=Location, color=Location), fill="white", size=1) +
  scale_color_manual(values=c("indianred", "darkolivegreen4", "darkolivegreen4"))+
  scale_shape_manual(values=c(21, 22, 24))+
    ylim(0,200) +
  theme_classic() +
  ylab(expression(paste("Phosphorus (",~ mu, "g/L)")))+
  xlab("Date") +
  ggtitle("E") +
  theme(axis.title = element_text(size=8), axis.text=element_text(size=7),
        legend.title = element_text(size = 8), 
        legend.key.size = unit(0.5, 'cm'), legend.text = element_text(size=7)) #+
  scale_x_date(breaks = scales::breaks_pretty(10))




## Nitrogen

MB_N <- Nut_Fig_Data %>%
  filter(Station == "MB") %>%
  select(Location, Date, Water_TN_mgL) %>%
  group_by(Location, Date) %>%
  summarize(Water_TN_mgL = mean(Water_TN_mgL)) %>%
  pivot_wider(names_from="Location", values_from = "Water_TN_mgL") %>%
  select(-IWC) %>%
  na.omit()

MB_TDN <- Nut_Fig_Data %>%
  select(Water_TDN_mgL, Date, Station) %>%
  filter(Station == "MB") %>%
  na.omit() %>%
  group_by(Date) %>%
  summarize(Water_TDN_mgL = mean(Water_TDN_mgL))


MB_SesN <- Nut_Fig_Data %>%
  select(N_mgL, Date, Station) %>%
  filter(Station == "MB") %>%
  na.omit() %>%
  group_by(Date) %>%
  summarize(N_mgL = mean(N_mgL))

MB_N <- full_join(MB_N, MB_SesN, by=c("Date")) %>%
  full_join(., MB_TDN, by=c("Date")) %>%
  pivot_longer(cols=c("N_mgL", "bottom", "surface", "Water_TDN_mgL"), names_to = "Location", values_to = "TN_mgL") %>%
  mutate(Location = if_else(Location == "bottom", "Water TN - 2.5m", Location),
         Location = if_else(Location == "surface", "Water TN - 0.5m", Location),
         Location = if_else(Location == "N_mgL", "Seston TN - IWC", Location),
         Location = if_else(Location == "Water_TDN_mgL", "Water TDN - IWC", Location))

MB_N_Fig <- MB_N %>%
  mutate(Date=as.Date(Date))%>%
  filter(Date > as.Date("2021-06-01") & Date <= as.Date("2021-11-01")) %>%
  ggplot() + 
    annotate("rect", xmin = as.Date("2021-06-01"), xmax = as.Date("2021-08-07"), ymin = 0, ymax = 2.5,
           fill = "grey91") +
  annotate("rect", xmin = as.Date("2021-08-07"), xmax = as.Date("2021-08-12"), ymin = 0, ymax =2.5,
           fill = "grey98") +
  annotate("rect", xmin = as.Date("2021-08-12"), xmax = as.Date("2021-08-20"), ymin = 0, ymax = 2.5,
           fill = "grey91") +
  annotate("rect", xmin = as.Date("2021-08-20"), xmax = as.Date("2021-08-24"), ymin = 0, ymax = 2.5,
           fill = "grey98") +
    annotate("rect", xmin = as.Date("2021-08-24"), xmax = as.Date("2021-09-03"), ymin = 0, ymax = 2.5,
           fill = "grey91") +
    annotate("rect", xmin = as.Date("2021-09-03"), xmax = as.Date("2021-09-15"), ymin = 0, ymax = 2.5,
           fill = "grey98") +
    annotate("rect", xmin = as.Date("2021-09-15"), xmax = as.Date("2021-09-27"), ymin = 0, ymax = 2.5,
           fill = "grey91") +
    annotate("rect", xmin = as.Date("2021-09-27"), xmax = as.Date("2021-10-31"), ymin = 0, ymax = 2.5,
           fill = "grey98") +
  geom_line(aes(x = Date, y = TN_mgL, color=Location), size = 0.75) + 
  geom_point(aes(x=Date, y=TN_mgL, shape=Location, color=Location), fill="white", size=1) +
  scale_color_manual(values=c("indianred", "dodgerblue4", "darkolivegreen4", "darkolivegreen4"))+
  scale_shape_manual(values=c(21, 21, 22, 24))+
    ylim(0,2.5) +
  theme_classic() +
  ylab("Nitrogen (mg/L)")+
  xlab("") +
  ggtitle("C") +
  theme(axis.title = element_text(size=8), axis.text=element_text(size=7),
        legend.title = element_text(size = 8), 
        legend.key.size = unit(0.5, 'cm'), legend.text = element_text(size=7))# +
  scale_x_date(breaks = scales::breaks_pretty(10))


## Carbon


MB_C <- Nut_Fig_Data %>%
  filter(Station == "MB") %>%
  select(Date,  Water_DOC_mgL)%>%
  na.omit() %>%
  group_by(Date) %>%
  summarize(Water_DOC_mgL = mean(Water_DOC_mgL))

MB_SesC <- Nut_Fig_Data %>%
  select(C_mgL, Date, Station) %>%
  filter(Station == "MB") %>%
  na.omit() %>%
  group_by(Date) %>%
  summarize(C_mgL = mean(C_mgL))

MB_C <- full_join(MB_C, MB_SesC, by=c("Date")) %>%
  pivot_longer(cols=c("C_mgL", "Water_DOC_mgL"), names_to = "Location", values_to = "C_mgL") %>%
  mutate(Location = if_else(Location == "Water_DOC_mgL", "Water DOC - IWC", Location),
         Location = if_else(Location == "C_mgL", "Seston C - IWC", Location))

MB_C_Fig <- MB_C %>%
  mutate(Date=as.Date(Date))%>%
  filter(Date > as.Date("2021-06-01") & Date <= as.Date("2021-11-01")) %>%
  ggplot() + 
    annotate("rect", xmin = as.Date("2021-06-01"), xmax = as.Date("2021-08-07"), ymin = 0, ymax = 8,
           fill = "grey91") +
  annotate("rect", xmin = as.Date("2021-08-07"), xmax = as.Date("2021-08-12"), ymin = 0, ymax =8,
           fill = "grey98") +
  annotate("rect", xmin = as.Date("2021-08-12"), xmax = as.Date("2021-08-20"), ymin = 0, ymax = 8,
           fill = "grey91") +
  annotate("rect", xmin = as.Date("2021-08-20"), xmax = as.Date("2021-08-24"), ymin = 0, ymax = 8,
           fill = "grey98") +
    annotate("rect", xmin = as.Date("2021-08-24"), xmax = as.Date("2021-09-03"), ymin = 0, ymax = 8,
           fill = "grey91") +
    annotate("rect", xmin = as.Date("2021-09-03"), xmax = as.Date("2021-09-15"), ymin = 0, ymax = 8,
           fill = "grey98") +
    annotate("rect", xmin = as.Date("2021-09-15"), xmax = as.Date("2021-09-27"), ymin = 0, ymax = 8,
           fill = "grey91") +
    annotate("rect", xmin = as.Date("2021-09-27"), xmax = as.Date("2021-10-31"), ymin = 0, ymax = 8,
           fill = "grey98") +
  geom_line(aes(x = Date, y = C_mgL, color=Location), size = 0.75) + 
  geom_point(aes(x=Date, y=C_mgL, shape=Location, color=Location), fill="white", size=1) +
  scale_color_manual(values=c("indianred", "dodgerblue4"))+
  scale_shape_manual(values=c(21, 21))+
  ylim(0,8) +
  theme_classic() +
  ylab("Carbon (mg/L)")+
  xlab("") +
  ggtitle("A") +
  theme(axis.title = element_text(size=8), axis.text=element_text(size=7),
        legend.title = element_text(size = 8), 
        legend.key.size = unit(0.5, 'cm'), legend.text = element_text(size=7)) #+
  scale_x_date(breaks = scales::breaks_pretty(10))


## Make these plots in Figure Sheet.
```

### St. Albans Bay

#### Temperature

```{r}
SA_Profiler <- read_csv("./Clean Data/SA_Profiler_2021_Clean.csv") %>%
  filter(Month >= 6 & Month < 11) %>%
  mutate(Date = make_date(Year, Month, Day)) %>%
  mutate(Group = if_else(Date >= as.Date("2021-06-17") & Date <= as.Date("2021-08-20"), 1, 0),
         Group = if_else(Date >= as.Date("2021-08-21") & Date <= as.Date("2021-09-06"), 2, Group),
         Group = if_else(Date >= as.Date("2021-09-08") & Date <= as.Date("2021-10-01"), 3, Group),
         Group = if_else(Date == as.Date("2021-10-04"), 4, Group),
         Group = if_else(Date >= as.Date("2021-10-06") & Date <= as.Date("2021-10-14"), 5, Group),
         Group = if_else(Date >= as.Date("2021-10-18") & Date <= as.Date("2021-10-21"), 6, Group),
         Group = if_else(Date >= as.Date("2021-10-23") & Date <= as.Date("2021-10-25"), 7, Group),
         Group = if_else(Date >= as.Date("2021-10-28") & Date <= as.Date("2021-10-30"), 8, Group)) %>%
  select(-Date, -Remove)


SA_Temp <- SA_Profiler %>%
  select(Depth, datetime, Temp_C, Month, Day, Year, Group) %>%
  filter(Depth == 0.5 | Depth == 4.5) %>%
  group_by(Depth, datetime, Group) %>%
  summarize(Temp_C = mean(Temp_C)) %>%
  mutate(Depth = as.character(Depth)) %>%
  ggplot(aes(x=datetime, y=Temp_C, color=Depth, group=Group)) + 
 annotate("rect", xmin = as_datetime("2021-06-01 00:00:00"), xmax = as_datetime("2021-07-11 00:00:00"), ymin = 0, ymax = 30,fill = "grey91") +
  annotate("rect", xmin = as_datetime("2021-07-11 00:00:00"), xmax = as_datetime("2021-07-15 00:00:00"), ymin = 0, ymax =30,fill = "grey98") +
  annotate("rect", xmin = as_datetime("2021-07-15 00:00:00"), xmax = as_datetime("2021-07-27 00:00:00"), ymin = 0, ymax = 30,fill = "grey91") +
  annotate("rect", xmin = as_datetime("2021-07-27 00:00:00"), xmax = as_datetime("2021-08-16 00:00:00"), ymin = 0, ymax = 30, fill = "grey98") +
  annotate("rect", xmin = as_datetime("2021-08-16 00:00:00"), xmax = as_datetime("2021-08-27 00:00:00"), ymin = 0, ymax = 30, fill = "grey91") +
  annotate("rect", xmin = as_datetime("2021-08-27 00:00:00"), xmax = as_datetime("2021-10-31 00:00:00"), ymin = 0, ymax = 30, fill = "grey98") +
  annotate(geom="text", x= as_datetime("2021-06-05 00:00:00"), y=31, label="PrB",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-07-12 00:00:00"), y=31, label="BC1",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-07-18 00:00:00"), y=31, label="E",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-07-30 00:00:00"), y=31, label="PB",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-08-20 00:00:00"), y=31, label="BC2",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-09-01 00:00:00"), y=31, label="PoB",
           color="black", size=1.4) +
  geom_line(size = 0.5) + 
  scale_color_manual(values=c("orangered3", "dodgerblue3"))+
  theme_classic() +
  ggtitle("B")+
  ylab("")+
  xlab("") +
  xlim(as_datetime("2021-06-01 00:00:00"), as_datetime("2021-10-31 23:59:59")) +
    theme(axis.title = element_text(size=8), axis.text=element_text(size=7),
        legend.title = element_text(size = 8), 
        legend.key.size = unit(0.5, 'cm'), legend.text = element_text(size=7), legend.position = "none",
        plot.title = element_text(size=9),
        plot.margin = unit(c(0, 0, 0, 0), 
                           "cm"))

```

```{r}

SA_DO <- SA_Profiler %>%
  select(Depth, datetime, ODOmgL, Month, Day, Year, Group) %>%
  filter(Depth == 0.5 | Depth == 4.5) %>%
  group_by(Depth, datetime, Group) %>%
  summarize(DO = mean(ODOmgL)) %>%
  mutate(Depth = as.character(Depth)) %>%
  ggplot(aes(x=datetime, y=DO, color=Depth, group=Group)) +
    annotate("rect", xmin = as_datetime("2021-06-01 00:00:00"), xmax = as_datetime("2021-07-11 00:00:00"), ymin = 0, ymax = 20,fill = "grey91") +
  annotate("rect", xmin = as_datetime("2021-07-11 00:00:00"), xmax = as_datetime("2021-07-15 00:00:00"), ymin = 0, ymax =20,fill = "grey98") +
  annotate("rect", xmin = as_datetime("2021-07-15 00:00:00"), xmax = as_datetime("2021-07-27 00:00:00"), ymin = 0, ymax = 20,fill = "grey91") +
  annotate("rect", xmin = as_datetime("2021-07-27 00:00:00"), xmax = as_datetime("2021-08-16 00:00:00"), ymin = 0, ymax = 20, fill = "grey98") +
  annotate("rect", xmin = as_datetime("2021-08-16 00:00:00"), xmax = as_datetime("2021-08-27 00:00:00"), ymin = 0, ymax = 20, fill = "grey91") +
  annotate("rect", xmin = as_datetime("2021-08-27 00:00:00"), xmax = as_datetime("2021-10-31 00:00:00"), ymin = 0, ymax = 20, fill = "grey98") +
  annotate(geom="text", x= as_datetime("2021-06-05 00:00:00"), y=20.6, label="PrB",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-07-12 00:00:00"), y=20.6, label="BC1",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-07-18 00:00:00"), y=20.6, label="E",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-07-30 00:00:00"), y=20.6, label="PB",
           color="black", size=1.4)+
  annotate(geom="text", x= as_datetime("2021-08-20 00:00:00"), y=20.6, label="BC2",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-09-01 00:00:00"), y=20.6, label="PoB",
           color="black", size=1.4) +
  geom_line(size = 0.5) + 
  scale_color_manual(values=c("orangered3", "dodgerblue3"))+
  theme_classic() +
  ggtitle("D")+
  ylab("")+
  xlab("") +
   theme(axis.title = element_text(size=8), axis.text=element_text(size=7),
        legend.title = element_text(size = 8), 
        legend.key.size = unit(0.5, 'cm'), legend.text = element_text(size=7), legend.position = "none",
        plot.title = element_text(size=9),
        plot.margin = unit(c(0, 0, 0, 0), 
                           "cm"))
```
#### Stability

```{r}
SA_bathy <- approx.bathy(Zmax = 12, lkeArea= 7200000, Zmean = 8, method = "voldev", zinterval = 0.5) #Approximates bathymetry (Cone or Voldev)
names(SA_bathy)[2] <- "areas" #Needs this column name to work with rlakeanalyzer


SA_Schmidt <- SA_Profiler %>%
  select(Depth, datetime, Temp_C, Month, Day, Year, Group) %>%
  group_by(Depth, datetime, Month, Day, Year, Group) %>%
  summarize(Temp_C = mean(Temp_C)) %>%
  group_by(datetime, Group) %>%
  mutate(SS = schmidt.stability(wtr = Temp_C, depths = Depth, bthA = MB_bathy$areas, bthD = MB_bathy$depths)) %>%
  select(datetime, SS, Group) %>%
  unique()

SA_SS <- SA_Schmidt %>%
  filter(SS > -100) %>%
  ggplot(aes(x=datetime, y=SS, group=Group)) +
     annotate("rect", xmin = as_datetime("2021-06-01 00:00:00"), xmax = as_datetime("2021-07-11 00:00:00"), ymin = 0, ymax = 25,fill = "grey91") +
  annotate("rect", xmin = as_datetime("2021-07-11 00:00:00"), xmax = as_datetime("2021-07-15 00:00:00"), ymin = 0, ymax =25,fill = "grey98") +
  annotate("rect", xmin = as_datetime("2021-07-15 00:00:00"), xmax = as_datetime("2021-07-27 00:00:00"), ymin = 0, ymax = 25,fill = "grey91") +
  annotate("rect", xmin = as_datetime("2021-07-27 00:00:00"), xmax = as_datetime("2021-08-16 00:00:00"), ymin = 0, ymax = 25, fill = "grey98") +
  annotate("rect", xmin = as_datetime("2021-08-16 00:00:00"), xmax = as_datetime("2021-08-27 00:00:00"), ymin = 0, ymax = 25, fill = "grey91") +
  annotate("rect", xmin = as_datetime("2021-08-27 00:00:00"), xmax = as_datetime("2021-10-31 00:00:00"), ymin = 0, ymax = 25, fill = "grey98") +
  annotate(geom="text", x= as_datetime("2021-06-05 00:00:00"), y=25.8, label="PrB",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-07-12 00:00:00"), y=25.8, label="BC1",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-07-18 00:00:00"), y=25.8, label="E",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-07-30 00:00:00"), y=25.8, label="PB",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-08-20 00:00:00"), y=25.8, label="BC2",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-09-01 00:00:00"), y=25.8, label="PoB",
           color="black", size=1.4) +
  geom_line()+
  theme_classic()+ 
  ylab(bquote('')) +
  xlab("") +
  ggtitle("F")+
  xlim(as_datetime("2021-06-01 00:00:00"), as_datetime("2021-10-31 23:59:59")) +
  theme(axis.title = element_text(size=8), axis.text=element_text(size=7),
        legend.title = element_text(size = 8), 
        legend.key.size = unit(0.5, 'cm'), legend.text = element_text(size=7),
        plot.title = element_text(size=9),
        plot.margin = unit(c(0, 0, 0, 0), 
                           "cm"))
 
```

#### Stream Gauge Flow
```{r}

SA_SF_MR <- dataRetrieval::importRDB1("https://nwis.waterservices.usgs.gov/nwis/iv/?sites=04292750&parameterCd=00060&startDT=2017-06-01T00:00:00.000-04:00&endDT=2021-10-31T23:59:59.999-04:00&siteStatus=all&format=rdb")  %>%
  mutate(Year = year(datetime),
         Month = month(datetime),
         Day = day(datetime)) %>%
  dplyr::group_by(Day, Month, Year) %>%
  dplyr::summarise(Avg_SF = mean(X67354_00060)) %>%
  mutate(Date = make_date(Year, Month, Day)) %>%
  filter(Month >= 6 & Month <= 11)

SA_SF_JB <- dataRetrieval::importRDB1("https://nwis.waterservices.usgs.gov/nwis/iv/?sites=04292810&parameterCd=00060&startDT=2017-06-01T00:00:00.000-04:00&endDT=2021-10-31T23:59:59.999-04:00&siteStatus=all&format=rdb")  %>%
  mutate(Year = year(datetime),
         Month = month(datetime),
         Day = day(datetime)) %>%
  dplyr::group_by(Day, Month, Year) %>%
  dplyr::summarise(Avg_SF = mean(X67363_00060)) %>%
  mutate(Date = make_date(Year, Month, Day)) %>%
  filter(Month >= 6 & Month <= 11)


Precip_Data_SA <- full_join(SA_SF_MR, SA_SF_JB) %>%
  group_by(Day, Month, Year, Date) %>%
  summarise(Sum_SF = sum(Avg_SF))


SA_SF <- Precip_Data_SA %>%
  filter(Year == 2021) %>%
  ggplot(aes(x=Date, y=Sum_SF))+
 annotate("rect", xmin = as.Date("2021-06-01"), xmax = as.Date("2021-07-11"), ymin = 0, ymax = 400,
           fill = "grey91") +
  annotate("rect", xmin = as.Date("2021-07-11"), xmax = as.Date("2021-07-15"), ymin = 0, ymax =400,
           fill = "grey98") +
  annotate("rect", xmin = as.Date("2021-07-15"), xmax = as.Date("2021-07-27"), ymin = 0, ymax = 400,
           fill = "grey91") +
  annotate("rect", xmin = as.Date("2021-07-27"), xmax = as.Date("2021-08-16"), ymin = 0, ymax = 400,
           fill = "grey98") +
  annotate("rect", xmin = as.Date("2021-08-16"), xmax = as.Date("2021-08-27"), ymin = 0, ymax = 400,
           fill = "grey91") +
  annotate("rect", xmin = as.Date("2021-08-27"), xmax = as.Date("2021-10-31"), ymin = 0, ymax = 400,
           fill = "grey98") +
  annotate(geom="text", x= as.Date("2021-06-05"), y=410, label="PrB",
           color="black", size=1.4) +
  annotate(geom="text", x= as.Date("2021-07-12"), y=410, label="BC1",
           color="black", size=1.4) +
  annotate(geom="text", x= as.Date("2021-07-18"), y=410, label="E",
           color="black", size=1.4) +
  annotate(geom="text", x= as.Date("2021-07-30"), y=410, label="PB",
           color="black", size=1.4) +
  annotate(geom="text", x= as.Date("2021-08-20"), y=410, label="BC2",
           color="black", size=1.4) +
  annotate(geom="text", x= as.Date("2021-09-01"), y=410, label="PoB",
           color="black", size=1.4) +
  geom_line(linewidth=1)+
  theme_classic()+ 
  ylab("") +
  xlab("") +
  ggtitle("J")+
  theme(axis.title = element_text(size=8), axis.text=element_text(size=7),
        legend.title = element_text(size = 8), 
        legend.key.size = unit(0.5, 'cm'), legend.text = element_text(size=7),
        plot.title = element_text(size=9),
        plot.margin = unit(c(0, 0, 0, 0), 
                           "cm"))


## identifying early june nitrogen delivery source

precip_SA <- Precip_Data_SA %>%
  mutate(month = month(Date)) %>%
  filter(Year == 2021) %>%
  filter(month == 8) %>%
  ggplot(aes(x=Date, y=Sum_SF))+
   geom_line(linewidth=1)+
  theme_classic()

```

#### Wind Speed and Direction
```{r}
SA_Met <- read_csv("./Clean Data/SA_Met_Clean.csv") %>%
  select(Year, Month, Datetime, Wind_Dir, Wind_Speed_m.s, Temp) %>%
  filter(Year == 2021)

SA21Wind <- SA_Met %>%
  filter(Month>=6 & Month < 11) %>%
  filter(Year == 2021) %>%
  ggplot(aes(x=Datetime, y=Wind_Speed_m.s)) +
   annotate("rect", xmin = as_datetime("2021-06-01 00:00:00"), xmax = as_datetime("2021-07-11 00:00:00"), ymin = 0, ymax = 10,fill = "grey91") +
  annotate("rect", xmin = as_datetime("2021-07-11 00:00:00"), xmax = as_datetime("2021-07-15 00:00:00"), ymin = 0, ymax =10,fill = "grey98") +
  annotate("rect", xmin = as_datetime("2021-07-15 00:00:00"), xmax = as_datetime("2021-07-27 00:00:00"), ymin = 0, ymax = 10,fill = "grey91") +
  annotate("rect", xmin = as_datetime("2021-07-27 00:00:00"), xmax = as_datetime("2021-08-16 00:00:00"), ymin = 0, ymax = 10, fill = "grey98") +
  annotate("rect", xmin = as_datetime("2021-08-16 00:00:00"), xmax = as_datetime("2021-08-27 00:00:00"), ymin = 0, ymax = 10, fill = "grey91") +
  annotate("rect", xmin = as_datetime("2021-08-27 00:00:00"), xmax = as_datetime("2021-10-31 00:00:00"), ymin = 0, ymax = 10, fill = "grey98") +
  annotate(geom="text", x= as_datetime("2021-06-05 00:00:00"), y=10.25, label="PrB",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-07-12 00:00:00"), y=10.25, label="BC1",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-07-18 00:00:00"), y=10.25, label="E",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-07-30 00:00:00"), y=10.25, label="PB",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-08-20 00:00:00"), y=10.25, label="BC2",
           color="black", size=1.4) +
  annotate(geom="text", x= as_datetime("2021-09-01 00:00:00"), y=10.25, label="PoB",
           color="black", size=1.4) +
  geom_spline(linewidth=0.5) +
  theme_classic() +
  ggtitle("H") +
  ylab("") +
  ylim(0,10.5) +
  xlab("") +
  #scale_x_date(breaks=pretty_breaks(n=6)) +
  theme(axis.title = element_text(size=8), axis.text=element_text(size=7),
        legend.title = element_text(size = 8), 
        legend.key.size = unit(0.5, 'cm'), legend.text = element_text(size=7),
        plot.title = element_text(size=9),
        plot.margin = unit(c(0, 0, 0, 0), 
                           "cm"))

SA_WindDir <- SA_Met %>%
  filter(Wind_Dir >= 0) %>%
  filter(Month>=6 & Month < 11) %>%
  filter(Year == 2021) %>%
  ggplot(aes(x=Datetime, y=Wind_Dir)) +
  geom_spline(linewidth=0.5) +
  theme_classic() +
  ggtitle("E") +
  ylab("Wind Direction") +
  xlab("") +
  #scale_x_date(breaks=pretty_breaks(n=6)) +
  theme(plot.title = element_text(hjust = 0, size=7), axis.title = element_text(size=7), axis.text=element_text(size=6),
        legend.title = element_text(size = 5), 
        legend.key.size = unit(0.07, 'in'), legend.text = element_text(size=3.8))
```

#### Air Temperature
```{r}
SA_AirTemp <- SA_Met %>%
  filter(Month>=6 & Month < 11) %>%
  filter(Year == 2021) %>%
  ggplot(aes(x=Datetime, y=Temp)) +
  geom_spline(linewidth=0.5) +
  theme_classic() +
  ggtitle("F") +
  ylab("Air Temperature (C)") +
  xlab("") +
  #scale_x_date(breaks=pretty_breaks(n=6)) +
  theme(plot.title = element_text(hjust = 0, size=7), axis.title = element_text(size=7), axis.text=element_text(size=6),
        legend.title = element_text(size = 5), 
        legend.key.size = unit(0.07, 'in'), legend.text = element_text(size=3.8))

```


#### pH
```{r}
SA_pH <- SA_Profiler %>%
  select(Depth, datetime, pH, Month, Day, Year) %>%
  filter(Month >= 6 & Month < 11) %>%
  ggplot(aes(x=datetime, y=pH, group=Group)) + 
  geom_spline(size = 1) + 
  theme_classic() +
  ggtitle("H")+
  ylab("pH")+
  xlab("") +
  theme(plot.title = element_text(hjust = 0, size=7), axis.title = element_text(size=7), axis.text=element_text(size=6),
        legend.title = element_text(size = 5), 
        legend.key.size = unit(0.07, 'in'), legend.text = element_text(size=3.8))

```

#### DOM Flourescence. 
```{r}

SA_DOM <- SA_Profiler %>%
  select(Depth, datetime, fDOM_RFU, Month, Day, Year) %>%
  filter(Month >= 6 & Month < 11) %>%
  ggplot(aes(x=datetime, y=fDOM_RFU, group=Group)) + 
  geom_spline(size = 1.00) + 
  scale_color_manual(values=c("orangered3", "cadetblue4"))+
  theme_classic() +
  ggtitle("A")+
  ylab("Flourescent DOM (RFU)")+
  xlab("") +
  theme(plot.title = element_text(hjust = 0, size=7), axis.title = element_text(size=7), axis.text=element_text(size=6),
        legend.title = element_text(size = 5), 
        legend.key.size = unit(0.07, 'in'), legend.text = element_text(size=3.8))
```
Make these publication plots in a separate R script. 

## Nutrient Plots: 

```{r}

### Load Data

Nut_Fig_Data <- All_Combined %>%
  select(-Anatoxin, -Microcystin)


## Missisquoi Bay


# Phosphorus

SA_P <- Nut_Fig_Data %>%
  filter(Station == "SA") %>%
  select(Location, Date, Water_TP_mgL) %>%
  mutate(Water_TP_ugL = Water_TP_mgL * 1000) %>%
  group_by(Location, Date) %>%
  summarize(Water_TP_ugL = mean(Water_TP_ugL)) %>%
  pivot_wider(names_from="Location", values_from = "Water_TP_ugL") %>%
  select(-IWC) %>%
  na.omit()

SA_SesP <- Nut_Fig_Data %>%
  select(SestonP_ugL, Date, Station) %>%
  filter(Station == "SA") %>%
  na.omit() %>%
  group_by(Date) %>%
  dplyr::summarize(SestonP_ugL = mean(SestonP_ugL))

SA_P <- full_join(SA_P, SA_SesP, by=c("Date")) %>%
  pivot_longer(cols=c("SestonP_ugL", "bottom", "surface"), names_to = "Location", values_to = "TP_ugL") %>%
  mutate(Location = if_else(Location == "bottom", "Water TP - 4.5m", Location),
         Location = if_else(Location == "surface", "Water TP - 0.5m", Location),
         Location = if_else(Location == "SestonP_ugL", "Seston TP - IWC", Location))

SA_P_Fig <- SA_P %>%
  mutate(Date=as.Date(Date))%>%
  filter(Date > as.Date("2021-06-01") & Date <= as.Date("2021-11-01")) %>%
  ggplot() + 
  annotate("rect", xmin = as.Date("2021-06-01"), xmax = as.Date("2021-07-11"), ymin = 0, ymax = 200,
           fill = "grey91") +
  annotate("rect", xmin = as.Date("2021-07-11"), xmax = as.Date("2021-07-15"), ymin = 0, ymax =200,
           fill = "grey98") +
  annotate("rect", xmin = as.Date("2021-07-15"), xmax = as.Date("2021-07-27"), ymin = 0, ymax = 200,
           fill = "grey91") +
  annotate("rect", xmin = as.Date("2021-07-27"), xmax = as.Date("2021-08-16"), ymin = 0, ymax = 200,
           fill = "grey98") +
  annotate("rect", xmin = as.Date("2021-08-16"), xmax = as.Date("2021-08-27"), ymin = 0, ymax = 200,
           fill = "grey91") +
  annotate("rect", xmin = as.Date("2021-08-27"), xmax = as.Date("2021-10-31"), ymin = 0, ymax = 200,
           fill = "grey98") +
  geom_line(aes(x = Date, y = TP_ugL, color=Location), size = 0.75) + 
  geom_point(aes(x=Date, y=TP_ugL, shape=Location, color=Location), fill="white", size=1) +
  scale_color_manual(values=c("indianred", "darkolivegreen4", "darkolivegreen4"))+
  scale_shape_manual(values=c(21, 22, 24))+
  theme_classic() +
  ylim(0, 200) +
  ylab("")+
  xlab("Date") +
  ggtitle("F") +
  theme(axis.title = element_text(size=8), axis.text=element_text(size=7),
        legend.title = element_text(size = 8), 
        legend.key.size = unit(0.5, 'cm'), legend.text = element_text(size=7))# +
  scale_x_date(breaks = scales::breaks_pretty(5))




## Nitrogen

SA_N <- Nut_Fig_Data %>%
  filter(Station == "SA") %>%
  select(Location, Date, Water_TN_mgL) %>%
  group_by(Location, Date) %>%
  summarize(Water_TN_mgL = mean(Water_TN_mgL)) %>%
  pivot_wider(names_from="Location", values_from = "Water_TN_mgL") %>%
  select(-IWC) %>%
  na.omit()

SA_TDN <- Nut_Fig_Data %>%
  select(Water_TDN_mgL, Date, Station) %>%
  filter(Station == "SA") %>%
  na.omit() %>%
  group_by(Date) %>%
  summarize(Water_TDN_mgL = mean(Water_TDN_mgL))


SA_SesN <- Nut_Fig_Data %>%
  select(N_mgL, Date, Station) %>%
  filter(Station == "SA") %>%
  na.omit() %>%
  group_by(Date) %>%
  summarize(N_mgL = mean(N_mgL))

SA_N <- full_join(SA_N, SA_SesN, by=c("Date")) %>%
  full_join(., SA_TDN, by=c("Date")) %>%
  pivot_longer(cols=c("N_mgL", "bottom", "surface", "Water_TDN_mgL"), names_to = "Location", values_to = "TN_mgL") %>%
  mutate(Location = if_else(Location == "bottom", "Water TN - 4.5m", Location),
         Location = if_else(Location == "surface", "Water TN - 0.5m", Location),
         Location = if_else(Location == "N_mgL", "Seston TN - IWC", Location),
         Location = if_else(Location == "Water_TDN_mgL", "Water TDN - IWC", Location))

SA_N_Fig <- SA_N %>%
  mutate(Date=as.Date(Date))%>%
  filter(Date > as.Date("2021-06-01") & Date <= as.Date("2021-11-01")) %>%
  ggplot() + 
   annotate("rect", xmin = as.Date("2021-06-01"), xmax = as.Date("2021-07-11"), ymin = 0, ymax = 2.5,
           fill = "grey91") +
  annotate("rect", xmin = as.Date("2021-07-11"), xmax = as.Date("2021-07-15"), ymin = 0, ymax =2.5,
           fill = "grey98") +
  annotate("rect", xmin = as.Date("2021-07-15"), xmax = as.Date("2021-07-27"), ymin = 0, ymax = 2.5,
           fill = "grey91") +
  annotate("rect", xmin = as.Date("2021-07-27"), xmax = as.Date("2021-08-16"), ymin = 0, ymax = 2.5,
           fill = "grey98") +
  annotate("rect", xmin = as.Date("2021-08-16"), xmax = as.Date("2021-08-27"), ymin = 0, ymax = 2.5,
           fill = "grey91") +
  annotate("rect", xmin = as.Date("2021-08-27"), xmax = as.Date("2021-10-31"), ymin = 0, ymax = 2.5,
           fill = "grey98") +
  geom_line(aes(x = Date, y = TN_mgL, color=Location), size = 0.75) + 
  geom_point(aes(x=Date, y=TN_mgL, shape=Location, color=Location), fill="white", size=1) +
  scale_color_manual(values=c("indianred", "dodgerblue4", "darkolivegreen4", "darkolivegreen4"))+
  scale_shape_manual(values=c(21, 21, 22, 24))+
  theme_classic() +
  ylim(0, 2.5) +
  ylab("")+
  xlab("") +
  ggtitle("D") +
  theme(axis.title = element_text(size=8), axis.text=element_text(size=7),
        legend.title = element_text(size = 8), 
        legend.key.size = unit(0.5, 'cm'), legend.text = element_text(size=7))# +
  scale_x_date(breaks = scales::breaks_pretty(10))


## Carbon


SA_C <- Nut_Fig_Data %>%
  filter(Station == "SA") %>%
  select(Date,  Water_DOC_mgL)%>%
  na.omit() %>%
  group_by(Date) %>%
  summarize(Water_DOC_mgL = mean(Water_DOC_mgL))

SA_SesC <- Nut_Fig_Data %>%
  select(C_mgL, Date, Station) %>%
  filter(Station == "SA") %>%
  na.omit() %>%
  group_by(Date) %>%
  summarize(C_mgL = mean(C_mgL))

SA_C <- full_join(SA_C, SA_SesC, by=c("Date")) %>%
  pivot_longer(cols=c("C_mgL", "Water_DOC_mgL"), names_to = "Location", values_to = "C_mgL") %>%
  mutate(Location = if_else(Location == "Water_DOC_mgL", "Water DOC - IWC", Location),
         Location = if_else(Location == "C_mgL", "Seston C - IWC", Location))

SA_C_Fig <- SA_C %>%
  mutate(Date=as.Date(Date))%>%
  filter(Date > as.Date("2021-06-01") & Date <= as.Date("2021-11-01")) %>%
  ggplot() + 
   annotate("rect", xmin = as.Date("2021-06-01"), xmax = as.Date("2021-07-11"), ymin = 0, ymax = 8,
           fill = "grey91") +
  annotate("rect", xmin = as.Date("2021-07-11"), xmax = as.Date("2021-07-15"), ymin = 0, ymax =8,
           fill = "grey98") +
  annotate("rect", xmin = as.Date("2021-07-15"), xmax = as.Date("2021-07-27"), ymin = 0, ymax = 8,
           fill = "grey91") +
  annotate("rect", xmin = as.Date("2021-07-27"), xmax = as.Date("2021-08-16"), ymin = 0, ymax = 8,
           fill = "grey98") +
  annotate("rect", xmin = as.Date("2021-08-16"), xmax = as.Date("2021-08-27"), ymin = 0, ymax = 8,
           fill = "grey91") +
  annotate("rect", xmin = as.Date("2021-08-27"), xmax = as.Date("2021-10-31"), ymin = 0, ymax = 8,
           fill = "grey98") +
  geom_line(aes(x = Date, y = C_mgL, color=Location), size = 0.75) + 
  geom_point(aes(x=Date, y=C_mgL, shape=Location, color=Location), fill="white", size=1) +
  scale_color_manual(values=c("indianred", "dodgerblue4"))+
  scale_shape_manual(values=c(21, 21))+
  theme_classic() +
  ylim(0,8) +
  ylab("")+
  xlab("") +
  ggtitle("B") +
  theme(axis.title = element_text(size=8), axis.text=element_text(size=7),
        legend.title = element_text(size = 8), 
        legend.key.size = unit(0.5, 'cm'), legend.text = element_text(size=7))# +
  scale_x_date(breaks = scales::breaks_pretty(10))


## Make these plots in Figure Sheet.
```


#### Statistics

### Water Temperature

```{r}
SA_Temp_Stats1 <- SA_Profiler %>%
  select(Depth, datetime, Temp_C, Month, Day, Year, Group) %>%
  mutate(Site = "SA") %>%
  filter(Depth == 1.0) %>%
  group_by(Depth, datetime, Site) %>%
  summarize(Temp_C = mean(Temp_C))


MB_Temp_Stats1 <- MB_Profiler %>%
  select(Depth, datetime, Temp_C, Month, Day, Year, Group) %>%
  mutate(Site = "MB") %>%
  filter(Depth == 1.0) %>%
  group_by(Depth, datetime, Site) %>%
  rename(Depth = Depth) %>%
  summarize(Temp_C = mean(Temp_C))

Temp_Stats_1 <- inner_join(SA_Temp_Stats1, MB_Temp_Stats1, by="datetime") %>%
  na.omit()

SA_Stats_1 <- Temp_Stats_1 %>%
  select(datetime, Site.x, Temp_C.x) %>%
  rename(Site = Site.x, 
         Temp_C = Temp_C.x)

MB_Stats_1 <- Temp_Stats_1 %>%
  select(datetime, Site.y, Temp_C.y) %>%
  rename(Site = Site.y, 
         Temp_C = Temp_C.y)

Temp_Stats_1 <- bind_rows(SA_Stats_1, MB_Stats_1) %>%
  na.omit()


### Normality: 

shapiro.test(SA_Stats_1$Temp_C)

shapiro.test(MB_Stats_1$Temp_C)


# Paired Samples Wilcoxon Test
result = wilcox.test(Temp_C ~ Site,
                    data = Temp_Stats_1,
                    paired = FALSE,
                    alternative = "two.sided")

# Printing the results
print(result)




Temp_Stats_1 %>%
  group_by(Site) %>%
  summarise(Avg = mean(Temp_C),
            sd = sd(Temp_C))

### Bottom Water Temperatures

SA_Temp_StatsBot <- SA_Profiler %>%
  select(Depth, datetime, Temp_C, Month, Day, Year, Group) %>%
  mutate(Site = "SA") %>%
  filter(Depth == 4.5) %>%
  group_by(Depth, datetime, Site) %>%
  summarize(Temp_C = mean(Temp_C))


MB_Temp_StatsBot<- MB_Profiler %>%
  select(Depth, datetime, Temp_C, Month, Day, Year, Group) %>%
  mutate(Site = "MB") %>%
  filter(Depth == 2.5) %>%
  group_by(Depth, datetime, Site) %>%
  rename(Depth = Depth) %>%
  summarize(Temp_C = mean(Temp_C))

Temp_Stats_Bot <- inner_join(SA_Temp_StatsBot, MB_Temp_StatsBot, by="datetime") %>%
  na.omit()

SA_Stats_Bot <- Temp_Stats_Bot %>%
  select(datetime, Site.x, Temp_C.x) %>%
  rename(Site = Site.x, 
         Temp_C = Temp_C.x)

MB_Stats_Bot <- Temp_Stats_Bot %>%
  select(datetime, Site.y, Temp_C.y) %>%
  rename(Site = Site.y, 
         Temp_C = Temp_C.y)

Temp_Stats_Bot <- bind_rows(SA_Stats_Bot, MB_Stats_Bot) %>%
  na.omit()

### Normality: 

shapiro.test(SA_Stats_Bot$Temp_C)

shapiro.test(MB_Stats_Bot$Temp_C)



# Paired Samples Wilcoxon Test
result = wilcox.test(Temp_C ~ Site,
                    data = Temp_Stats_Bot,
                    paired = FALSE,
                    alternative = "two.sided")

# Printing the results
print(result)
4.035e-11*6

### Averages and sd

Temp_Stats_Bot %>%
  group_by(Site) %>%
  summarise(Avg = mean(Temp_C),
            sd = sd(Temp_C))



### Difference in water column temperatures. 

SA_Temp_Stats_Diff <- SA_Profiler %>%
  select(Depth, datetime, Temp_C, Month, Day, Year, Group) %>%
  mutate(Site = "SA") %>%
  filter(Depth == 1.0 | Depth == 4.5) %>%
  group_by(Depth, datetime, Site) %>%
  summarize(Temp_C = mean(Temp_C)) %>%
  pivot_wider(names_from = Depth, values_from = Temp_C) %>%
  mutate(Diff= `4.5`-`1`) %>%
  select(datetime, Diff, Site)


MB_Temp_Stats_Diff <- MB_Profiler %>%
  select(Depth, datetime, Temp_C, Month, Day, Year) %>%
  mutate(Site = "MB") %>%
  filter(Depth == 1.0 | Depth == 2.5) %>%
  group_by(Depth, datetime, Site) %>%
  rename(Depth = Depth) %>%
  summarize(Temp_C = mean(Temp_C)) %>%
  pivot_wider(names_from = Depth, values_from = Temp_C)  %>%
  mutate(Diff = `2.5`-`1`) %>%
  select(datetime, Diff, Site)


Temp_Stats_Diff <- inner_join(SA_Temp_Stats_Diff, MB_Temp_Stats_Diff, by="datetime") 

SA_Stats_Diff <- Temp_Stats_Diff %>%
  select(datetime, Site.x, Diff.x) %>%
  rename(Site = Site.x, 
         Diff = Diff.x)

MB_Stats_Diff <- Temp_Stats_Diff %>%
  select(datetime, Site.y, Diff.y) %>%
  rename(Site = Site.y, 
         Diff = Diff.y)

Temp_Stats_Diff <- bind_rows(SA_Temp_Stats_Diff, MB_Temp_Stats_Diff) %>%
  na.omit()


### Normality: 

shapiro.test(SA_Stats_Diff$Diff)

shapiro.test(MB_Stats_Diff$Diff)


# Paired Samples Wilcoxon Test
result = wilcox.test(Diff ~ Site,
                    data = Temp_Stats_Diff,
                    paired = FALSE,
                    alternative = "two.sided")

# Printing the results
print(result)

2.2e-16*6
Temp_Stats_Diff %>%
  group_by(Site) %>%
  summarise(Avg = mean(Diff),
            sd = sd(Diff))

```

### Wind Speed

```{r}
SA_Wind_Stats <- SA_Met %>%
  select(Datetime, Wind_Speed_m.s, Month, Year) %>%
  mutate(Day = day(Datetime)) %>%
  mutate(Date = make_date(Year, Month, Day)) %>%
  mutate(Site = "SA") %>%
  rename(Wind_Speed = Wind_Speed_m.s) %>%
  filter(Month>=6 & Month < 11) %>%
  mutate(Group = if_else(Date < as.Date("2021-09-30"), 1, 0),
         Group = if_else(Date >= as.Date("2021-10-11"), 2, Group)) %>%
  filter(Group != 0) %>%
  select(-Group, -Date, -Month, -Day, -Year)

MB_Wind_Stats <- MB_Met %>%
  select(Datetime, Wind_Speed, Month) %>%
  mutate(Site = "MB") %>%
  filter(Month>=6 & Month < 11) %>%
  select(-Month)

Wind_Stats <- bind_rows(MB_Wind_Stats, SA_Wind_Stats) %>%
  na.omit()

shapiro.test(MB_Wind_Stats$Wind_Speed)


# Paired Samples Wilcoxon Test
result = wilcox.test(Wind_Speed ~ Site,
                    data = Wind_Stats,
                    paired = FALSE,
                    alternative = "two.sided")

# Printing the results
print(result)
2.36e-05*6

Wind_Stats %>%
  group_by(Site) %>%
  summarise(Avg = mean(Wind_Speed),
            sd = sd(Wind_Speed))




```

### Schmidt Stability

```{r}

SA_SS_Stats <- SA_Schmidt %>%
  select(datetime, SS) %>%
  mutate(Site = "SA") %>%
  mutate(SS = if_else(SS < 0, 0, SS))

MB_SS_Stats <- MB_Schmidt %>%
  select(datetime, SS) %>%
  mutate(Site = "MB") %>%
  mutate(SS = if_else(SS < 0, 0, SS))


SS_Stats <- inner_join(SA_SS_Stats, MB_SS_Stats, by="datetime") %>%
  na.omit()

SA_SS_Stats <- SS_Stats %>%
  select(datetime, Site.x, SS.x) %>%
  rename(Site = Site.x, 
         SS = SS.x)

MB_SS_Stats <- SS_Stats %>%
  select(datetime, Site.y, SS.y) %>%
  rename(Site = Site.y, 
         SS = SS.y)

SS_Stats <- bind_rows(SA_SS_Stats, MB_SS_Stats) %>%
  na.omit()


shapiro.test(MB_SS_Stats$SS)
shapiro.test(SA_SS_Stats$SS)

# Paired Samples Wilcoxon Test
result = wilcox.test(SS ~ Site,
                    data = SS_Stats,
                    paired = FALSE,
                    alternative = "two.sided")

# Printing the results
print(result)
1.09e-12*6

SS_Stats %>%
  group_by(Site) %>%
  summarise(Avg = mean(SS),
            sd = sd(SS),
            max = max(SS))

```

### Stream Flow

```{r}

SA_SF_Stats <- Precip_Data_SA  %>%
  select(Date, Sum_SF) %>%
  mutate(Site = "SA")

MB_SF_Stats <- Precip_Data_MB  %>%
  select(Date, Sum_SF) %>%
  mutate(Site = "MB")

SF_Stats <- bind_rows(SA_SF_Stats, MB_SF_Stats) %>%
  na.omit()

shapiro.test(SA_SF_Stats$Sum_SF)
shapiro.test(MB_SF_Stats$Sum_SF)

# Paired Samples Wilcoxon Test
result = wilcox.test(Sum_SF ~ Site,
                    data = SF_Stats,
                    paired = FALSE,
                    alternative = "two.sided")

# Printing the results
print(result)
2.2e-16*4

SF_Stats %>%
  group_by(Site) %>%
  summarise(Avg = mean(Sum_SF),
            sd = sd(Sum_SF),
            max = max(Sum_SF))

```
## Bloom Stages Statistics:

Using the dates determined from hierarchal clustering below, we are going to create some statistics for the results section regarding trends in physical properties of the lake across bloom stages. 

Missisquoi Bay Dates:

2021-06-01 - 2021-08-07 pre bloom
2021-08-07 - 2021-08-12: Exponential Phase 1
2021-08-12 - 2021-08-20 : Peak Growth 1
2021-08-20 - 2021-08-24: Bloom Collapse 1
2021-08-24 - 2021-09-03 Exponential growth 2
2021-09-03 - 2021-09-15 Peak Growth 2
2021-09-15 - 2021-09-27 Bloom Collpase 2
2021-09-27 - 2021-10-31: Post-Bloom



```{r}

MB_Temp1_Stage <- MB_Temp_Stats1 %>%
  mutate(Stage = if_else(datetime <= as_datetime("2021-08-07 00:00:01"), "Pre-Bloom", "None"),
         Stage = if_else(datetime > as_datetime("2021-08-07 00:00:01") & datetime <= as_datetime("2021-08-12 00:00:01"), "Exponential Phase 1", Stage),
         Stage = if_else(datetime > as_datetime("2021-08-12 00:00:01") & datetime <= as_datetime("2021-08-20 00:00:01"), "Peak Growth 1", Stage),
         Stage = if_else(datetime > as_datetime("2021-08-20 00:00:01") & datetime <= as_datetime("2021-08-24 00:00:01"), "Bloom Collapse 1", Stage),
         Stage = if_else(datetime > as_datetime("2021-08-24 00:00:01") & datetime <= as_datetime("2021-09-03 00:00:01"), "Exponential Phase 2", Stage),
         Stage = if_else(datetime > as_datetime("2021-09-03 00:00:01") & datetime <= as_datetime("2021-09-15 00:00:01"), "Peak Growth 2", Stage),
         Stage = if_else(datetime > as_datetime("2021-09-15 00:00:01") & datetime <= as_datetime("2021-09-27 00:00:01"), "Bloom Collapse 2", Stage),
         Stage = if_else(datetime > as_datetime("2021-09-27 00:00:01"), "Post-Bloom", Stage)) 

MB_Temp1_Stage <- MB_Temp1_Stage %>%
  na.omit()

test <- aov(Temp_C~Stage, data=MB_Temp1_Stage)

summary(test)

TukeyHSD(test)


MB_Temp1_Stage %>%  
  group_by(Stage) %>%
  summarise(Avg = mean(Temp_C),
            sd = sd(Temp_C),
            max = max(Temp_C))
  
###

MB_Schmidt_Stage <-  MB_Schmidt %>% 
  mutate(Stage = if_else(datetime <= as_datetime("2021-08-07 00:00:01"), "Pre-Bloom", "None"),
         Stage = if_else(datetime > as_datetime("2021-08-07 00:00:01") & datetime <= as_datetime("2021-08-12 00:00:01"), "Exponential Phase 1", Stage),
         Stage = if_else(datetime > as_datetime("2021-08-12 00:00:01") & datetime <= as_datetime("2021-08-20 00:00:01"), "Peak Growth 1", Stage),
         Stage = if_else(datetime > as_datetime("2021-08-20 00:00:01") & datetime <= as_datetime("2021-08-24 00:00:01"), "Bloom Collapse 1", Stage),
         Stage = if_else(datetime > as_datetime("2021-08-24 00:00:01") & datetime <= as_datetime("2021-09-03 00:00:01"), "Exponential Phase 2", Stage),
         Stage = if_else(datetime > as_datetime("2021-09-03 00:00:01") & datetime <= as_datetime("2021-09-15 00:00:01"), "Peak Growth 2", Stage),
         Stage = if_else(datetime > as_datetime("2021-09-15 00:00:01") & datetime <= as_datetime("2021-09-27 00:00:01"), "Bloom Collapse 2", Stage),
         Stage = if_else(datetime > as_datetime("2021-09-27 00:00:01"), "Post-Bloom", Stage)) 

MB_Schmidt_Stage <- MB_Schmidt_Stage %>%
  mutate(SS = if_else(SS < 0, 0, SS)) %>%
  na.omit()

test <- aov(SS~Stage, data=MB_Schmidt_Stage)

summary(test)

TukeyHSD(test)


MB_Schmidt_Stage %>%  
  group_by(Stage) %>%
  summarise(Avg = mean(SS),
            sd = sd(SS),
            max = max(SS))
  

```


St. Albans Bay 

St. Albans Dates: 

2021-06-01 - 2021-07-11: Pre-Bloom
2021-07-11 - 2021-07-15: Pre-Bloom, Bloom Collapse
2021-07-15 - 2021-07-27: Exponential Growth
2021-07-27 - 2021-08-16: Peak Growth
2021-08-16 - 2021-08-27: Bloom Collapse
2021-08-27 - 2021-10-31: Post-bloom

```{r}

SA_Temp1_Stage <- SA_Temp_Stats1 %>%
  mutate(Stage = if_else(datetime <= as_datetime("2021-07-15 00:00:01"), "Pre-Bloom", "None"),
         Stage = if_else(datetime > as_datetime("2021-07-15 00:00:01") & datetime <= as_datetime("2021-07-27 00:00:01"), "Exponential Phase", Stage),
         Stage = if_else(datetime > as_datetime("2021-07-27 00:00:01") & datetime <= as_datetime("2021-08-16 00:00:01"), "Peak Growth", Stage),
         Stage = if_else(datetime > as_datetime("2021-08-16 00:00:01") & datetime <= as_datetime("2021-08-27 00:00:01"), "Bloom Collapse ", Stage),
         Stage = if_else(datetime > as_datetime("2021-08-27 00:00:01"), "Post-Bloom", Stage)) 

SA_Temp1_Stage <- SA_Temp1_Stage %>%
  na.omit() %>%
  mutate(Temp_C_S = scale(Temp_C))


test <- aov(Temp_C~Stage, data=SA_Temp1_Stage)

summary(test)

TukeyHSD(test)


SA_Temp1_Stage %>%  
  group_by(Stage) %>%
  summarise(Avg = mean(Temp_C),
            sd = sd(Temp_C),
            max = max(Temp_C))
  
###

SA_Schmidt_Stage <-  SA_Schmidt %>% 
  mutate(Stage = if_else(datetime <= as_datetime("2021-07-15 00:00:01"), "Pre-Bloom", "None"),
         Stage = if_else(datetime > as_datetime("2021-07-15 00:00:01") & datetime <= as_datetime("2021-07-27 00:00:01"), "Exponential Phase", Stage),
         Stage = if_else(datetime > as_datetime("2021-07-27 00:00:01") & datetime <= as_datetime("2021-08-16 00:00:01"), "Peak Growth", Stage),
         Stage = if_else(datetime > as_datetime("2021-08-16 00:00:01") & datetime <= as_datetime("2021-08-27 00:00:01"), "Bloom Collapse ", Stage),
         Stage = if_else(datetime > as_datetime("2021-08-27 00:00:01"), "Post-Bloom", Stage)) 

SA_Schmidt_Stage <- SA_Schmidt_Stage %>%
  mutate(SS = if_else(SS < 0, 0, SS)) %>%
  na.omit()

test <- aov(SS~Stage, data=SA_Schmidt_Stage)

summary(test)

TukeyHSD(test)


SA_Schmidt_Stage %>%  
  group_by(Stage) %>%
  summarise(Avg = mean(SS),
            sd = sd(SS),
            max = max(SS))
  

```


### Nutrients

# Phosphorus

```{r}
SA_P_Stats_S <- SA_P %>%
  mutate(Site = "SA") %>%
  filter(Location == "Water TP - 0.5m")

MB_P_Stats_S <- MB_P %>%
  mutate(Site = "MB") %>%
  filter(Location == "Water TP - 0.5m")


P_Stats_S <- rbind(SA_P_Stats_S, MB_P_Stats_S) %>%
  na.omit()

# Paired Samples Wilcoxon Test
result = t.test(TP_ugL ~ Site,
                    data = P_Stats_S,
                    paired = FALSE,
                    alternative = "two.sided")

# Printing the results
print(result)

P_Stats_S %>%
  group_by(Site) %>%
  summarise(Avg = mean(TP_ugL),
            sd = sd(TP_ugL),
            max = max(TP_ugL))



SA_P_Stats_B <- SA_P %>%
  mutate(Site = "SA") %>%
  filter(Location == "Water TP - 4.5m")

MB_P_Stats_B <- MB_P %>%
  mutate(Site = "MB") %>%
  filter(Location == "Water TP - 2.5m")


P_Stats_B <- rbind(SA_P_Stats_B, MB_P_Stats_B) %>%
  na.omit()

# Paired Samples Wilcoxon Test
result = t.test(TP_ugL ~ Site,
                    data = P_Stats_B,
                    paired = FALSE,
                    alternative = "two.sided")

# Printing the results
print(result)

P_Stats_B %>%
  group_by(Site) %>%
  summarise(Avg = mean(TP_ugL),
            sd = sd(TP_ugL),
            max = max(TP_ugL))

#####

SA_P_Stats_I <- SA_P %>%
  mutate(Site = "SA") %>%
  filter(Location == "Seston TP - IWC")

MB_P_Stats_I <- MB_P %>%
  mutate(Site = "MB") %>%
  filter(Location == "Seston TP - IWC")


P_Stats_I <- rbind(SA_P_Stats_I, MB_P_Stats_I) %>%
  na.omit()

# Paired Samples Wilcoxon Test
result = t.test(TP_ugL ~ Site,
                    data = P_Stats_I,
                    paired = FALSE,
                    alternative = "two.sided")

# Printing the results
print(result)

P_Stats_I %>%
  group_by(Site) %>%
  summarise(Avg = mean(TP_ugL),
            sd = sd(TP_ugL),
            max = max(TP_ugL))
```
# Nitrogen

```{r}
SA_N_Stats_S <- SA_N %>%
  mutate(Site = "SA") %>%
  filter(Location == "Water TN - 0.5m")

MB_N_Stats_S <- MB_N %>%
  mutate(Site = "MB") %>%
  filter(Location == "Water TN - 0.5m")


N_Stats_S <- rbind(SA_N_Stats_S, MB_N_Stats_S) %>%
  na.omit()

# Paired Samples Wilcoxon Test
result = t.test(TN_mgL ~ Site,
                    data = N_Stats_S,
                    paired = FALSE,
                    alternative = "two.sided")

# Printing the results
print(result)

N_Stats_S %>%
  group_by(Site) %>%
  summarise(Avg = mean(TN_mgL),
            sd = sd(TN_mgL),
            max = max(TN_mgL))



SA_N_Stats_B <- SA_N %>%
  mutate(Site = "SA") %>%
  filter(Location == "Water TN - 4.5m")

MB_N_Stats_B <- MB_N %>%
  mutate(Site = "MB") %>%
  filter(Location == "Water TN - 2.5m")


N_Stats_B <- rbind(SA_N_Stats_B, MB_N_Stats_B) %>%
  na.omit()

# Paired Samples Wilcoxon Test
result = t.test(TN_mgL ~ Site,
                    data = N_Stats_B,
                    paired = FALSE,
                    alternative = "two.sided")

# Printing the results
print(result)

N_Stats_B %>%
  group_by(Site) %>%
  summarise(Avg = mean(TN_mgL),
            sd = sd(TN_mgL),
            max = max(TN_mgL))

#####

SA_N_Stats_I <- SA_N %>%
  mutate(Site = "SA") %>%
  filter(Location == "Seston TN - IWC")

MB_N_Stats_I <- MB_N %>%
  mutate(Site = "MB") %>%
  filter(Location == "Seston TN - IWC")


N_Stats_I <- rbind(SA_N_Stats_I, MB_N_Stats_I) %>%
  na.omit()

# Paired Samples Wilcoxon Test
result = t.test(TN_mgL ~ Site,
                    data = N_Stats_I,
                    paired = FALSE,
                    alternative = "two.sided")

# Printing the results
print(result)

N_Stats_I %>%
  group_by(Site) %>%
  summarise(Avg = mean(TN_mgL),
            sd = sd(TN_mgL),
            max = max(TN_mgL))

#####

SA_DN_Stats_I <- SA_N %>%
  mutate(Site = "SA") %>%
  filter(Location == "Water TDN - IWC")

MB_DN_Stats_I <- MB_N %>%
  mutate(Site = "MB") %>%
  filter(Location == "Water TDN - IWC")


DN_Stats_I <- rbind(SA_DN_Stats_I, MB_DN_Stats_I) %>%
  na.omit()

# Paired Samples Wilcoxon Test
result = t.test(TN_mgL ~ Site,
                    data = DN_Stats_I,
                    paired = FALSE,
                    alternative = "two.sided")

# Printing the results
print(result)

DN_Stats_I %>%
  group_by(Site) %>%
  summarise(Avg = mean(TN_mgL),
            sd = sd(TN_mgL),
            max = max(TN_mgL))
```

# Carbon

```{r}
SA_C_Stats <- SA_C %>%
  mutate(Site = "SA") %>%
  filter(Location == "Water DOC - IWC")

MB_C_Stats <- MB_C %>%
  mutate(Site = "MB") %>%
  filter(Location == "Water DOC - IWC")



C_Stats <- rbind(SA_C_Stats, MB_C_Stats) %>%
  na.omit()

# Paired Samples Wilcoxon Test
result = t.test(C_mgL ~ Site,
                    data = C_Stats,
                    paired = FALSE,
                    alternative = "two.sided")

# Printing the results
print(result)

C_Stats %>%
  group_by(Site) %>%
  summarise(Avg = mean(C_mgL),
            sd = sd(C_mgL),
            max = max(C_mgL))



SA_C_Stats_S <- SA_C %>%
  mutate(Site = "SA") %>%
  filter(Location == "Seston C - IWC")

MB_C_Stats_S <- MB_C %>%
  mutate(Site = "MB") %>%
  filter(Location == "Seston C - IWC")



C_Stats_S <- rbind(SA_C_Stats_S, MB_C_Stats_S) %>%
  na.omit()

# Paired Samples Wilcoxon Test
result = t.test(C_mgL ~ Site,
                    data = C_Stats_S,
                    paired = FALSE,
                    alternative = "two.sided")

# Printing the results
print(result)

C_Stats_S %>%
  group_by(Site) %>%
  summarise(Avg = mean(C_mgL),
            sd = sd(C_mgL),
            max = max(C_mgL))


#####
```


#### Remodel Bloom Dynamics by Biomass?
Instead of utilizing phycocyanin in the logistic growth model, I wonder if I could make a few models with each individual cyanobacteria species....It will probably be tough due to the sparse samples, but we can see...

Otherwise, I may be able to do a cluster anlaysis to help define conditions related to blooms and categorize them that way. 



#### Toxins Standardized by potential toxic species abundance.

Reviewers suggested that I normalize the toxin data by the toxic cyanobacteria species present.

## Create Toxic vs Non-toxic Categories in Biomass data

```{r}
Phytos <- read_csv("./Clean Data/Warner_etal_Disturbance_PhytoplanktonBV.csv") %>%
  #filter(Taxonomic_group == "Cyanobacteria") %>%
  select(Sample_ID, SampleDate, Genus, species, BM_ug.L, RA_BM, Taxonomic_group) %>%
  mutate(SampleDate = if_else(Sample_ID == "IP21_074_SA", as.Date("2021-08-26"), SampleDate),
         SampleDate = if_else(Sample_ID == "IP21_065_SA", as.Date("2021-08-13"), SampleDate)) %>%
  mutate(Date = SampleDate) %>%
  mutate(Station = if_else(grepl("MB", Sample_ID), "MB", "SA"))

# unique list of cyanos

Phytos %>%
  select(Genus, species) %>%
  unique()

# Biomass of each group of Toxin Producers

Phytos_ATX <- Phytos %>%
  filter(Genus == "Dolichospermum" | Genus == "Aphanizomenon" | Genus == "Cuspidothrix" | Genus == "Microcystis" |
           Genus == "Pseudoanabaena") %>%
  group_by(Sample_ID, SampleDate) %>%
  summarise(Sum_BM_ATX = sum(BM_ug.L))
  

Phytos_MC <- Phytos %>%
  filter(Genus == "Dolichospermum" |  Genus == "Microcystis" | Genus == "Anabaenopsis" | Genus == "Aphanocapsa" | Genus == "Calothrix" | 
        Genus == "Gloeotrichia" | Genus == "Pseudoanabaena" | Genus == "Merismopedia") %>%
  group_by(Sample_ID, SampleDate) %>%
  summarise(Sum_BM_MC = sum(BM_ug.L))


Phytos_Toxin_BM <- full_join(Phytos_ATX, Phytos_MC)

#replace NA with zeros

Phytos_Toxin_BM$Sum_BM_ATX <- replace_na(Phytos_Toxin_BM$Sum_BM_ATX, 0)
```

## Join Toxin Data with Phytplankton Data. 

To do this, we need to clean up the Sample ID, or create a new column with Site ID 

```{r}
Phytos_Toxin_BM <- Phytos_Toxin_BM %>%
  mutate(Station = if_else(grepl("MB", Sample_ID), "MB", "SA")) %>%
  mutate(Date = ymd(SampleDate)) %>%
  ungroup() %>%
  select(-Sample_ID, -SampleDate)

#read in toxin data
Toxins <- read.csv("Toxins_SAMB2021_Clean.csv") %>%
  mutate(Microcystin = if_else(is.na(Microcystin), 0, Microcystin),
         Anatoxin = if_else(is.na(Anatoxin), 0, Anatoxin)) %>%
  mutate(Date = mdy(Date)) %>%
  select(Date, Station, Anatoxin, Microcystin)

Phytos_Toxin_BM <- full_join(Phytos_Toxin_BM, Toxins) %>%
  na.omit() %>%
  mutate(ATX_Q = Anatoxin/Sum_BM_ATX,
         MC_Q = Microcystin/Sum_BM_MC) 

Phytos_Toxin_BM$ATX_Q[is.nan(Phytos_Toxin_BM$ATX_Q)]<-0

```


### Toxin Quota Statistics.

Steps: 
- Test for Normality
- Run Appropriate Tests
- Summary Statistics (Mean, SD, Max)


# Test for Normality
```{r}

shapiro.test(Phytos_Toxin_BM$ATX_Q)

shapiro.test(Phytos_Toxin_BM$MC_Q)

```
Both samples had P-values that were < 0.05, suggesting that the data is not normally distributed. Because the groups are independent of one another, we will run a Mann-Whitney U test.

```{r}
ATX_Q <- Phytos_Toxin_BM %>%
  filter(Anatoxin > 0)

MC_Q <- Phytos_Toxin_BM %>%
  filter(Microcystin > 0)

results <- wilcox.test(ATX_Q ~ Station, data = ATX_Q, exact = FALSE)
results

results <- wilcox.test(MC_Q ~ Station, data = MC_Q, exact = FALSE)
results

```

Overall, the results still are not statistically different...likely due to the high inflation of non-toxic samples. Though when we remove the samples where microcystin and anatoxin were both less than 0, there is still no significant difference in cyanotoxins...Which may be a result of low sample size. 


Visualize the Difference in toxicity via boxplots. 

```{r}
Phytos_Toxin_BM %>%
  select(ATX_Q, MC_Q, Station) %>%
  pivot_longer(cols=c(ATX_Q, MC_Q), values_to = "Q", names_to = "Toxin") %>%
  filter(Q > 0) %>%
  ggplot(aes(x=Toxin, y=Q, group=Station, color=Station)) +
  geom_jitter()

```
## Join PC and Toxins DF together

```{r}
Profiler_MB <- read_csv("MissisquoiWinch_PFL_Step_with_headers.csv") %>%
  mutate(datetime = mdy_hm(TIMESTAMP)) %>%
  mutate(Year = year(datetime)) %>%
  mutate(Month = month(datetime)) %>%
  mutate(Day = day(datetime)) %>%
  mutate(Hour = hour(datetime)) %>%
  mutate(Minute = 0) %>%
  mutate(datetime = make_datetime(Year, Month, Day, Hour, Minute)) %>%
  mutate(Date = make_date(Year, Month, Day)) %>%
  mutate(Depth = Depth_meters) %>%
  mutate(Depth = if_else(Depth <=0.8, 0.5, Depth)) %>%
  mutate(Depth = if_else(Depth >0.8 & Depth <=1.3, 1.0, Depth)) %>%
  mutate(Depth = if_else(Depth >1.3 & Depth <=1.8, 1.5, Depth)) %>%
  mutate(Depth = if_else(Depth >1.8 & Depth <=2.3, 2.0, Depth)) %>%
  mutate(Depth = if_else(Depth >2.3 & Depth <=2.8, 2.5, Depth)) %>%
  mutate(Depth = if_else(Depth >2.8 & Depth <=3.3, 3.0, Depth)) %>%
  filter(Depth < 3.0) %>%
  mutate(ODOmgL = `ODO_mg/L`) %>%
  mutate(ODOsat = `ODOsat_%`) %>%
  mutate(PC_RFU = `BGA_PC_RFU`) %>%
  mutate(Chl_RFU = `Chl_RFU`) %>%
  mutate(Turbid = `Turbid_NTU`) %>%
  mutate(Remove = if_else(Month == 9 & PC_RFU > 15, "Yes", "No")) %>%
  filter(Remove == "No") %>%
  select(datetime, Day, Month, Hour, Depth, Temp_C, ODOmgL, ODOsat, PC_RFU,
         Chl_RFU, pH, Month, Day, Year, Turbid) %>%
  mutate(Date = make_date(Year, Month, Day)) %>%
  group_by(Date) %>%
  summarise(PC_RFU = mean(PC_RFU)) %>%
  mutate(Station = "MB") 


Profiler_SA <- read_csv("StAlbansInner_PFL_Step_with_headers.csv") %>%
  mutate(datetime = mdy_hm(TIMESTAMP)) %>%
  mutate(Year = year(datetime)) %>%
  mutate(Month = month(datetime)) %>%
  mutate(Day = day(datetime)) %>%
  mutate (Hour = hour(datetime)) %>%
  mutate(Minute = 0) %>%
  mutate(datetime = make_datetime(Year, Month, Day, Hour, Minute)) %>%
  mutate(Date = make_date(Year, Month, Day)) %>%
  mutate(Depth = Depth_meters) %>%
  mutate(Depth = if_else(Depth <=0.8, 0.5, Depth)) %>%
  mutate(Depth = if_else(Depth >0.8 & Depth <=1.3, 1.0, Depth)) %>%
  mutate(Depth = if_else(Depth >1.3 & Depth <=1.8, 1.5, Depth)) %>%
  mutate(Depth = if_else(Depth >1.8 & Depth <=2.3, 2.0, Depth)) %>%
  mutate(Depth = if_else(Depth >2.3 & Depth <=2.8, 2.5, Depth)) %>%
  mutate(Depth = if_else(Depth >2.8 & Depth <=3.3, 3.0, Depth)) %>%
  mutate(Depth = if_else(Depth >3.3 & Depth <=3.8, 3.5, Depth)) %>%
  mutate(Depth = if_else(Depth >3.8 & Depth <=4.3, 4.0, Depth)) %>%
  mutate(Depth = if_else(Depth >4.3 & Depth <=4.8, 4.5, Depth)) %>%
  mutate(ODOmgL = `ODO_mg/L`) %>%
  mutate(ODOsat = `ODOsat_%`) %>%
  mutate(PC_RFU = `BGA_PC_RFU`) %>%
  mutate(Chl_RFU = `Chl_RFU`) %>%
  mutate(Turbid = `Turbid_NTU`) %>%
  select(datetime, Day, Month, Hour, Depth, Temp_C, ODOmgL, ODOsat, 
         PC_RFU, Chl_RFU, pH, Month, Day, Year, Turbid) %>%
  mutate(Date = make_date(Year, Month, Day)) %>%
  group_by(Date) %>%
  summarise(PC_RFU = mean(PC_RFU)) %>%
  mutate(Station = "SA")


Profiler_PC <- rbind(Profiler_MB, Profiler_SA)


Toxins_PC <- full_join(Phytos_Toxin_BM, Profiler_PC, by=c("Date", "Station"))

```


### Toxic Cyanos over time with toxins.

Join toxin DF with species df

```{r}
Phytos_Toxin <- left_join(Phytos, Phytos_Toxin_BM) %>%
  na.omit() %>%
  filter(Genus == "Dolichospermum" | Genus == "Aphanizomenon" | Genus == "Cuspidothrix" | Genus == "Microcystis" |
           Genus == "Pseudoanabaena" | Genus == "Anabaenopsis" | Genus == "Aphanocapsa" | Genus == "Calothrix" | 
        Genus == "Gloeotrichia" | Genus == "Merismopedia") %>%
  group_by(Station, Date, ATX_Q, MC_Q, Genus) %>%
  summarise(BM = sum(BM_ug.L)) %>%
  pivot_longer(cols=c(ATX_Q, MC_Q), values_to = "Q", names_to = "Toxin")

Phytos_Toxin %>%
  filter(Station == "MB") %>%
  ggplot() +
  geom_bar(aes(x=Date, y=Q, fill=Toxin), stat="identity", position="dodge", width=4, alpha=.4) +
  geom_line(aes(x = Date, y = BM/120000000, color=Genus, group = Genus), size = 0.5) + 
  #geom_point(aes(x = Date, y = BM/120000000, color=Genus, group = Genus), size = 0.5) + 
  scale_fill_manual(values=c("orangered3", "cadetblue4"))+
  #scale_y_continuous(sec.axis = sec_axis(~.*120000000, name = "")) +
  theme_classic() 

Phytos_Toxin %>%
  filter(Station == "MB") %>%
  filter(Genus != "Dolichospermum") %>%
  filter(Date < as.Date("2021-10-11")) %>%
  ggplot() +
  geom_bar(aes(x=Date, y=Q, fill=Toxin), stat="identity", position="dodge", alpha=0.15) +
  geom_line(aes(x = Date, y = BM/120000000, color=Genus, group = Genus), size = 0.5) + 
  geom_point(aes(x = Date, y = BM/120000000, color=Genus, group = Genus), size = 0.5) + 
  scale_fill_manual(values=c("orangered3", "cadetblue4"))+
  ylim(0, 0.00002) +
  scale_y_continuous(sec.axis = sec_axis(~.*120000000, name = "")) +
  theme_classic()

Phytos_Toxin %>%
  filter(Station == "SA") %>%
  filter(Genus == "Cuspidothrix" | Genus == "Aphanizomenon") %>%
  #filter(Date < as.Date("2021-10-11")) %>%
  ggplot() +
  geom_bar(aes(x=Date, y=Q, fill=Toxin), stat="identity", position="dodge", alpha=0.15) +
  geom_line(aes(x = Date, y = BM/1200000, color=Genus, group = Genus), size = 0.5) + 
  geom_point(aes(x = Date, y = BM/1200000, color=Genus, group = Genus), size = 0.5) + 
  scale_fill_manual(values=c("orangered3", "cadetblue4"))+
  ylim(0, 0.00002) +
  scale_y_continuous(sec.axis = sec_axis(~.*1200000, name = "")) +
  theme_classic()



```




#### Clustering for Cyanobacteria Bloom Stages.

For this I want to cluster based on Phytoplankton, but also the Seston Nutrients. I think that will help clearly define the growth stages of the blooms. 

```{r}
library(vegan)
library(BiodiversityR)
library(ggrepel)

MB_Phyto_Keep <- Phytos %>%
  filter(Station == "MB") %>%
  group_by(Sample_ID, SampleDate, Genus) %>%
  summarize(RA_BM = sum(RA_BM)) %>%
  mutate(Keep = if_else(RA_BM >= 0.05, "Yes", "No")) %>%
  ungroup() %>%
  select(Genus, Keep) %>%
  filter(Keep=="Yes") %>%
  unique()

MB_Phyto_Matrix <- Phytos %>%
  filter(Station == "MB") %>%
  filter(Genus %in% MB_Phyto_Keep$Genus) %>%
  select(SampleDate, Genus, BM_ug.L) %>%
  group_by(SampleDate, Genus) %>%
  summarise(BM = sum(BM_ug.L)) %>%
  pivot_wider(names_from = "Genus", values_from="BM") %>%
  filter(SampleDate > as.Date("2021-06-01")) %>%
  rename(Date = SampleDate)

MB_Phyto_Matrix[is.na(MB_Phyto_Matrix)] <- 0

MB_Seston_Matrix <- All_Combined %>%
  select(SestonP_uML, SestonC_uML, SestonN_uML, Station, Date) %>%
  filter(Station == "MB") %>%
  unique() %>%
  mutate(Seston_CP = SestonC_uML/SestonP_uML,
         Seston_CN = SestonC_uML/SestonN_uML, 
         Seston_NP = SestonN_uML/SestonP_uML) %>%
  na.omit() %>%
  select(-SestonP_uML, -SestonC_uML, -SestonN_uML, -Station) %>%
  mutate(Date = ymd(Date))

MB_Phyto_Matrix <- left_join(MB_Phyto_Matrix, MB_Seston_Matrix) %>%
  column_to_rownames(var="Date") %>% 
  na.omit()

### Bray Curtis

BC_MB <- vegdist(MB_Phyto_Matrix, method="bray")

##### St. Albans

SA_Phyto_Keep <- Phytos %>%
  filter(Station == "SA") %>%
  group_by(Sample_ID, SampleDate, Genus) %>%
  summarize(RA_BM = sum(RA_BM)) %>%
  mutate(Keep = if_else(RA_BM >= 0.05, "Yes", "No")) %>%
  ungroup() %>%
  select(Genus, Keep) %>%
  filter(Keep=="Yes") %>%
  unique()


SA_Phyto_Matrix <- Phytos %>%
  filter(Station == "SA") %>%
  filter(Genus %in% MB_Phyto_Keep$Genus) %>%
  select(SampleDate, Genus, BM_ug.L) %>%
  group_by(SampleDate, Genus) %>%
  summarise(BM = sum(BM_ug.L)) %>%
  pivot_wider(names_from = "Genus", values_from="BM") %>%
  filter(SampleDate > as.Date("2021-06-01")) %>%
  rename(Date = SampleDate)


SA_Phyto_Matrix[is.na(SA_Phyto_Matrix)] <- 0

SA_Seston_Matrix <- All_Combined %>%
  select(SestonP_uML, SestonC_uML, SestonN_uML, Station, Date) %>%
  filter(Station == "SA") %>%
  unique() %>%
  mutate(Seston_CP = SestonC_uML/SestonP_uML,
         Seston_CN = SestonC_uML/SestonN_uML, 
         Seston_NP = SestonN_uML/SestonP_uML) %>%
  na.omit() %>%
  select(-SestonP_uML, -SestonC_uML, -SestonN_uML, -Station) %>%
  mutate(Date = ymd(Date))


SA_Phyto_Matrix <- left_join(SA_Phyto_Matrix, SA_Seston_Matrix) %>%
  column_to_rownames(var="Date") %>% 
  na.omit()
### Bray Curtis

BC_SA <- vegdist(SA_Phyto_Matrix, method="bray")

```

Clustering the points based on the bray curtis dissimilarity matrix. 
```{r}
MB_clust <- hclust(BC_MB, method="ward.D2")  

SA_clust <- hclust(BC_SA, method="ward.D2")

plot(MB_clust, las = 1, 
     main="Cluster diagram of MB Genus", 
     xlab="Sample", 
     ylab="Bray Curtis Dissimilarity")


plot(SA_clust, las = 1, 
     main="Cluster diagram of SA Genera", 
     xlab="Sample", 
     ylab="Bray Curtis Dissimilarity")

```

Optimizing number of clusters.
```{r}
library(factoextra)


# Plot cluster results
p1 <- fviz_nbclust(as.matrix(BC_MB), FUN = hcut, method = "wss",  k.max = 8) +
  ggtitle("(A) Elbow method")

p2 <- fviz_nbclust(as.matrix(BC_MB), FUN = hcut, method = "silhouette", k.max = 8) +
  ggtitle("(B) Silhouette method")

p3 <- fviz_nbclust(as.matrix(BC_MB), FUN = hcut, method = "gap_stat", k.max = 8) +
  ggtitle("(C) Gap statistic")

# Display plots side by side
gridExtra::grid.arrange(p1, p2, p3, nrow = 1)


## Cut the tree based on number of clusters


fviz_dend(
  MB_clust,
  k = 2,
  horiz = TRUE,
  rect = TRUE,
  rect_fill = TRUE,
  rect_border = "jco",
  k_colors = "jco",
  cex = 1
)


# Plot cluster results
p1 <- fviz_nbclust(as.matrix(BC_SA), FUN = hcut, method = "wss",  k.max = 8) +
  ggtitle("(A) Elbow method")

p2 <- fviz_nbclust(as.matrix(BC_SA), FUN = hcut, method = "silhouette", k.max = 8) +
  ggtitle("(B) Silhouette method")

p3 <- fviz_nbclust(as.matrix(BC_SA), FUN = hcut, method = "gap_stat", k.max = 8) +
  ggtitle("(C) Gap statistic")

# Display plots side by side
gridExtra::grid.arrange(p1, p2, p3, nrow = 1)


fviz_dend(
  SA_clust,
  k = 3,
  horiz = TRUE,
  rect = TRUE,
  rect_fill = TRUE,
  rect_border = "jco",
  k_colors = "jco",
  cex = 1
)
?fviz_dend
```
Plotting the clustered groups with phytoplankton dates to see what they might represent. 
```{r}
### Found color pallette through jco in ggsci

Phytos %>%
  filter(Station == "MB") %>%
  filter(Genus %in% MB_Phyto_Keep$Genus) %>%
  filter(Taxonomic_group == "Cyanobacteria") %>%
  group_by(Date) %>%
  summarise(BM = sum(BM_ug.L)) %>%
  unique() %>%
  filter(Date > as.Date("2021-06-01")) %>%
  mutate(Group = if_else(Date == as.Date("2021-08-10") | Date == as.Date("2021-08-19") | Date == as.Date("2021-08-25") | Date == as.Date("2021-09-17") | Date == as.Date("2021-09-03") | Date == as.Date("2021-09-10"), 1, 0),
         Group = if_else(Date == as.Date("2021-06-29") | Date == as.Date("2021-08-03") | Date == as.Date("2021-10-11"), 2, Group)) %>%
  ggplot(aes(x=Date, y=BM)) +
  geom_line() + 
  geom_point(aes(color=as.character(Group))) + 
  scale_color_manual(values=c("black", "#EFC000FF", "#0073C2FF")) +
  theme_classic() 



Phytos %>%
  filter(Station == "SA") %>%
  filter(Genus %in% SA_Phyto_Keep$Genus) %>%
  filter(Taxonomic_group == "Cyanobacteria") %>%
  group_by(Date) %>%
  summarise(BM = sum(BM_ug.L)) %>%
  unique() %>%
  filter(Date > as.Date("2021-06-01")) %>%
  mutate(Group = if_else(Date == as.Date("2021-08-13") | Date == as.Date("2021-07-27"), 1, 0),
         Group = if_else(Date == as.Date("2021-08-19") | Date == as.Date("2021-08-03") | Date == as.Date("2021-09-03") | Date == as.Date("2021-08-26") | Date == as.Date("2021-09-17"), 2, Group),
         Group = if_else(Date == as.Date("2021-07-22") | Date == as.Date("2021-07-13") | Date == as.Date("2021-10-11"), 3, Group)) %>%
  ggplot(aes(x=Date, y=BM)) +
  geom_line() + 
  geom_point(aes(color=as.character(Group))) + 
  scale_color_manual(values=c("black", "#0073C2FF", "#EFC000FF",  "#868686FF")) +
  theme_classic()

```


Hierarchal clustering analyses was used to determine bloom periods from non-bloom periods in the phytoplankton genera data and seston nutrient data utilizing the bray-curtis dissmilarity between each sample. The number of clusters to use was verified using the elbow, silhouette and gap statistic methods. The methods did  not converge on the same number of clusters, but utilizing the elbow plot and the silhoutte plot, we landed on two main clusters to separate the season... The clusters grouped into right before and right after the bloom, and the  main bloom period. 


St. Albans clustering wasn't as clear as Missisquoi Bays. Each graph indicated a different number of clusters to use to group the species data, ranging from 1-3 clusters. Therefore, we chose the 3 clusters, as it best separated the data into groups that we were looking for. The hierarchal clustering again created a group that included the main bloom period, with a clear beginning and end of the bloom, but the bloom period was split into two groups, which were mainly defined as having differences in Aulacoseira abundance.

## Phycocyanin, CHL, Rate of Change, and 3 day prior conditions for Clustering, pH, Turbidity. 

I want to try to cluster the samples in the same way I did before, 

## Missisquoi Bay.
```{r}

#### Phycocyanin

MB_PC_Matrix <- MB_Profiler %>%
  filter(Month > 6 & Month < 10) %>%
  select(PC_RFU, pH, Day, Month, Year, Chl_RFU) %>%
  mutate(Date = make_date(Year, Month, Day)) %>%
  group_by(Date) %>%
  summarize(PC = mean(PC_RFU),
            pH = mean(pH), 
            CHL = mean(Chl_RFU)) %>%
  mutate(Lag3_PC = lag(PC, n=3L),
         Lag3_CHL = lag(CHL, n=3L),
         Lag1_PC = lag(PC),
         Lag1_CHL = lag(CHL)) %>%
  na.omit() %>%
  mutate(ROC_PC = (PC-Lag1_PC)/Lag1_PC, 
         ROC_CHL = (CHL-Lag1_CHL)/Lag1_CHL) %>%
  select(Date, PC, CHL, Lag3_PC, Lag3_CHL, ROC_PC, ROC_CHL) %>%
  column_to_rownames(var="Date") %>% 
  na.omit()


library(vegan)
### Cluster Analysis. 

MB_PC_Euc <- vegdist(MB_PC_Matrix, method="euclidean")


MB_PC_clust <- hclust(MB_PC_Euc, method="ward.D2")  

## Visualize Cluster


plot(MB_PC_clust, las = 1, 
     main="Cluster diagram of MB PC and CHL", 
     xlab="Date", 
     ylab="Euclidean Distance")

```
## Testing number of clusters


```{r}
library(factoextra)


# Plot cluster results
p1_MB <- fviz_nbclust(as.matrix(MB_PC_Euc), FUN = hcut, method = "wss",  k.max = 10) +
  ggtitle("(A) Elbow method")

p2 <- fviz_nbclust(as.matrix(MB_PC_Euc), FUN = hcut, method = "silhouette", k.max = 10) +
  ggtitle("(B) Silhouette method")

p3 <- fviz_nbclust(as.matrix(MB_PC_Euc), FUN = hcut, method = "gap_stat", k.max = 10) +
  ggtitle("(C) Gap statistic")

# Display plots side by side
MB_K <- gridExtra::grid.arrange(p1, p2, p3, nrow = 1)

```

```{r}
fviz_dend(
  MB_PC_clust,
  k = 3,
  horiz = TRUE,
  rect = TRUE,
  rect_fill = TRUE,
  rect_border = "jco",
  k_colors = "jco",
  main = "A",
  cex = 0.75,
  ylab = "") +
  theme_classic()



```
Extracting Groups and Coloring points based on them. 


```{r}

cut_avg <- cutree(MB_PC_clust, k = 4)
MB_PC <- mutate(MB_PC_Matrix, cluster = cut_avg) %>%
  rownames_to_column(var="Date")

MB_PC %>%
  ggplot(aes(x=as_date(Date), y=PC)) +
  geom_line(color="black") +
  geom_point(aes(group=as.factor(cluster), color=as.factor(cluster))) +
  theme_classic()
  
MB_PC %>%
  ggplot(aes(x=as_date(Date), y=CHL)) +
  geom_line(color="black") +
  geom_point(aes(group=as.factor(cluster), color=as.factor(cluster))) +
  theme_classic()
  

```
This clustering method did a really nice job of highlight periods of rapid growth change - so both the rapid increase and decrease...albeit it didn't capture the second bloom collapes (when you add an additional cluster it does), but thats because it was so rapid. K=4.


## St. Albans

```{r}

#### Phycocyanin

SA_PC_Matrix <- SA_Profiler %>%
  filter(Month > 5 & Month < 12) %>%
  select(PC_RFU, pH, Day, Month, Year, Chl_RFU) %>%
  mutate(Date = make_date(Year, Month, Day)) %>%
  group_by(Date) %>%
  summarize(PC = mean(PC_RFU),
            pH = mean(pH), 
            CHL = mean(Chl_RFU)) %>%
  mutate(Lag3_PC = lag(PC, n=3L),
         Lag3_CHL = lag(CHL, n=3L),
         Lag1_PC = lag(PC),
         Lag1_CHL = lag(CHL)) %>%
  na.omit() %>%
  mutate(ROC_PC = (PC-Lag1_PC)/Lag1_PC, 
         ROC_CHL = (CHL-Lag1_CHL)/Lag1_CHL) %>%
  select(Date, PC, CHL, Lag3_PC, Lag3_CHL, ROC_PC, ROC_CHL, -pH) %>%
  column_to_rownames(var="Date") %>% 
  na.omit()


library(vegan)
### Cluster Analysis. 

SA_PC_Euc <- vegdist(SA_PC_Matrix, method="euclidean")


SA_PC_clust <- hclust(SA_PC_Euc, method="ward.D2")  



## Visualize Cluster


plot(SA_PC_clust, las = 1, 
     main="Cluster diagram of MB PC and CHL", 
     xlab="Date", 
     ylab="Euclidean Distance")

```

```{r}
fviz_dend(
  SA_PC_clust,
  k = 3,
  horiz = TRUE,
  rect = TRUE,
  rect_fill = TRUE,
  rect_border = "jco",
  k_colors = "jco",
  main = "A",
  cex = 0.75,
  ylab = "") +
  theme_classic()



```
Extracting Groups and Coloring points based on them. 

## Testing the number of clusters.

```{r}
library(factoextra)


# Plot cluster results
p1_SA <- fviz_nbclust(as.matrix(SA_PC_Euc), FUN = hcut, method = "wss",  k.max = 10) +
  ggtitle("(A) Elbow method")

p2 <- fviz_nbclust(as.matrix(SA_PC_Euc), FUN = hcut, method = "silhouette", k.max = 10) +
  ggtitle("(B) Silhouette method")

p3 <- fviz_nbclust(as.matrix(SA_PC_Euc), FUN = hcut, method = "gap_stat", k.max = 10) +
  ggtitle("(C) Gap statistic")

# Display plots side by side
gridExtra::grid.arrange(p1, p2, nrow = 1)

```
```{r}
cut_avg <- cutree(SA_PC_clust, k =3)
SA_PC <- mutate(SA_PC_Matrix, cluster = cut_avg) %>%
  rownames_to_column(var="Date")

SA_PC %>%
  ggplot(aes(x=as_date(Date), y=PC)) +
  geom_line(color="black") +
  geom_point(aes(group=as.factor(cluster), color=as.factor(cluster))) +
  theme_classic()
  
SA_PC %>%
  ggplot(aes(x=as_date(Date), y=CHL)) +
  geom_line(color="black") +
  geom_point(aes(group=as.factor(cluster), color=as.factor(cluster))) +
  theme_classic()
  

```



#### Toxic CCAs - Though this probably won't mean anything (:

#### RDA Analysis on Drivers of Bloom Dynamics: 

Next for this analysis, I want to specify the drivers of cyanobacteria species...

- Select Cyanobacteria Species
- Select Environmental Variables
-- Wind Speed, Stability, Surface PAR, (DN, DP - eventually) TDN, DOC, Turbidity, Seston CN, Seston CP, MC_Q, ATX_Q



## Missisquoi Bay

```{r}

## selecting phytoplankton that are > 5%

MB_Phyto_Date <- Phytos %>%
  filter(Station == "MB") %>%
  select(SampleDate) %>%
  unique()
  
MB_Phyto_Keep <- Phytos %>%
  filter(Station == "MB") %>%
  group_by(Sample_ID, SampleDate, Genus) %>%
  summarize(RA_BM = sum(RA_BM)) %>%
  mutate(Keep = if_else(RA_BM >= 0.05, "Yes", "No")) %>%
  ungroup() %>%
  select(Genus, Keep) %>%
  filter(Keep=="Yes") %>%
  unique()

MB_Phyto_Matrix <- Phytos %>%
  filter(Taxonomic_group == "Cyanobacteria") %>%
  filter(Station == "MB") %>%
  filter(Genus %in% MB_Phyto_Keep$Genus) %>%
  select(SampleDate, Genus, BM_ug.L) %>%
  group_by(SampleDate, Genus) %>%
  summarise(BM = sum(BM_ug.L)) %>%
  pivot_wider(names_from = "Genus", values_from="BM") %>%
  filter(SampleDate > as.Date("2021-06-01")) %>%
  rename(Date = SampleDate)

MB_Phyto_Matrix[is.na(MB_Phyto_Matrix)] <- 0

MB_Seston_Matrix <- All_Combined %>%
  select(SestonP_uML, SestonC_uML, SestonN_uML, Station, Date) %>%
  filter(Station == "MB") %>%
  unique() %>%
  mutate(Seston_CP = SestonC_uML/SestonP_uML,
         Seston_CN = SestonC_uML/SestonN_uML, 
         Seston_NP = SestonN_uML/SestonP_uML) %>%
  na.omit() %>%
  select(-SestonP_uML, -SestonC_uML, -SestonN_uML, -Station) %>%
  mutate(Date = ymd(Date)) %>%
    filter(Date %in% MB_Phyto_Date$SampleDate)

## Weather Matrix

MB_Wind_RDA <- MB_Met %>%
  select(Wind_Speed, Date) %>%
  filter(Date %in% MB_Phyto_Date$SampleDate) %>%
  group_by(Date) %>%
  summarize(Wind_Speed = mean(Wind_Speed))

MB_SS_RDA <- MB_Schmidt %>%
  mutate(Day = day(datetime),
         Month = month(datetime),
         Year = year(datetime),
         Date = make_date(Year, Month, Day)) %>%
  select(SS, Date) %>%
  filter(Date %in% MB_Phyto_Date$SampleDate) %>%
  group_by(Date) %>%
  summarize(SS = mean(SS))


# Water Temp

MB_WT_RDA <- MB_Profiler %>%
  mutate(Day = day(datetime),
         Month = month(datetime),
         Year = year(datetime),
         Date = make_date(Year, Month, Day)) %>%
  select(Temp_C, Date) %>%
  filter(Date %in% MB_Phyto_Date$SampleDate) %>%
  group_by(Date) %>%
  summarize(Temp_C = mean(Temp_C))

# Sum Stream Flow
MB_SF_RDA <- MB_SF_Stats %>%
  select(Sum_SF, Date) %>%
  filter(Date %in% MB_Phyto_Date$SampleDate) %>%
  group_by(Date) %>%
  summarize(Sum_SF = mean(Sum_SF)) 

## Dissolved Nutrients. 

DissNut_S <- read_xlsx("./DissolvedNutrients_2021.xlsx") %>%
  filter(site == "Miss Bay") %>%
  select(site, depth, rep, date, `NO3_mg/L`, `NH4_mg/L`, `PO4_mg/L`) %>%
  mutate(Date = ymd(date),
        depth = if_else(depth == "surface", "Surface", depth),
        depth = if_else(depth == "bottom", "Bottom", depth)) %>%
  mutate(NO3 = if_else(`NO3_mg/L` < 0, 0, `NO3_mg/L`),
         NH4 = if_else(`NH4_mg/L`< 0, 0, `NH4_mg/L`),
         PO4 = if_else(`PO4_mg/L` < 0, 0, `PO4_mg/L`),
         NO3 = NO3 * 1000,
         NH4 = NH4 * 1000,
         PO4 = PO4 * 1000,
         DIN = NO3 + NH4) %>%
    na.omit() %>%
  group_by(site, depth, Date) %>%
  filter(depth=="Surface") %>%
  summarize(NH4 = mean(NH4),
            NO3 = mean(NO3),
            PO4_S = mean(PO4),
            DIN_S = mean(DIN)) %>%
  ungroup() %>%
  select(DIN_S, PO4_S, Date)

DissNut_B <- read_xlsx("./DissolvedNutrients_2021.xlsx") %>%
  filter(site == "Miss Bay") %>%
  select(site, depth, rep, date, `NO3_mg/L`, `NH4_mg/L`, `PO4_mg/L`) %>%
  mutate(Date = ymd(date),
        depth = if_else(depth == "surface", "Surface", depth),
        depth = if_else(depth == "bottom", "Bottom", depth)) %>%
  mutate(NO3 = if_else(`NO3_mg/L` < 0, 0, `NO3_mg/L`),
         NH4 = if_else(`NH4_mg/L`< 0, 0, `NH4_mg/L`),
         PO4 = if_else(`PO4_mg/L` < 0, 0, `PO4_mg/L`),
         NO3 = NO3 * 1000,
         NH4 = NH4 * 1000,
         PO4 = PO4 * 1000,
         DIN = NO3 + NH4) %>%
    na.omit() %>%
  group_by(site, depth, Date) %>%
  filter(depth=="Bottom") %>%
  summarize(NH4 = mean(NH4),
            NO3 = mean(NO3),
            PO4_B = mean(PO4),
            DIN_B = mean(DIN)) %>%
  ungroup() %>%
  select(DIN_B, PO4_B, Date)
## Join together. 
  
MB_Env_RDA <- full_join(MB_SF_RDA, MB_Wind_RDA) %>%
  full_join(., MB_WT_RDA) %>%
  full_join(., MB_SS_RDA) %>%
  full_join(., DissNut_S) %>%
  full_join(., DissNut_B) %>%
  #full_join(., MB_Seston_Matrix) %>%
  na.omit()


MB_Phyto_RDA <- MB_Phyto_Matrix %>%
  filter(Date %in% MB_Env_RDA$Date) %>%
  column_to_rownames(var="Date")

MB_Phyto_RDA[is.na(MB_Phyto_RDA)] <- 0


MB_Env_RDA <-   MB_Env_RDA %>%
  rownames_to_column(var="Remove") %>%
  select(-Remove) %>%
  column_to_rownames(var="Date")
```

## Checking for Colinearity in Variables: 

```{r}

library(corrplot)

MB_Corr = cor(MB_Env_RDA)
corrplot(MB_Corr, method = 'number')

corrplot::cor

```
Using a threshold of 0.75, we will remove Dissolved inorganic nitrogen in the bottom waters. Though the relationship between wind is really interested. Suggesting internal N loading during low wind. 


## Run RDA. 

```{r}
library(BiodiversityR)

MB_Phyto_RDA <- MB_Phyto_RDA %>%
  select(-coccoid_cyano, -Gloeotrichia) %>%
  decostand("hellinger")

MB_Env_RDA <- MB_Env_RDA %>%
  decostand("standardize")


MB_dbrda <- dbrda(MB_Phyto_RDA ~ .,
                    data = MB_Env_RDA,
                  distance="bray")

print(MB_dbrda)

anova.cca(MB_dbrda)

```


Forward selection of the RDA


```{r}
# Initial RDA with ALL of the environmental data
MB_full <- dbrda(MB_Phyto_RDA ~ .,
                    data = MB_Env_RDA, 
                 distance="bray")

MB_null <- dbrda(MB_Phyto_RDA ~ 1, data=MB_Env_RDA, 
                 distance="bray")

modAIC <- MASS::stepAIC(MB_null,direction='forward', scope = list(lower = MB_null,
                                                              upper = MB_full))
summary(modAIC)


```
After running the forward selection model, bottom orthophosphate levels are the only important variable in Missisquoi Bay in Shaping the cyanobacteria community. 

```{r}
MB_mod <- dbrda(MB_Phyto_RDA ~ PO4_B, data=MB_Env_RDA, 
                 distance="bray")


```

```{r}
library(BiodiversityR)

MB_mod_summary <- summary(MB_mod)


MB_mod_summary$concont
```


```{r}

## This code adds species scores back into the dbrda, since they are always missing. That way we can plot species on our ordination plot with the sites and environmental variables. 

sppscores(MB_mod) <- MB_Phyto_RDA

plot <- ordiplot(MB_mod, type = "point")

```


```{r}
# This code chunk extracts data from the dbRDA

sites.long <- sites.long(plot, env.data=MB_Env_RDA) %>%
  select(PO4_B, axis1, axis2, labels)

axis.long <- axis.long(MB_mod, choices=c(1, 2))


## Edit the species.long dataframe to include a column with abundance, then order abundance, and filter out....keep the top 10 functional groups. 

df <- colSums(MB_Phyto_RDA) %>%
  as.data.frame() %>%
  mutate(`.` = abs(`.`))

## Find Top 10 Functional Groups. 

species.long <- species.long(plot)
species.long


vectors.envfit <- envfit(plot, env=MB_Env_RDA)
vectors.long <- vectorfit.long(vectors.envfit) %>%
  filter(vector == "PO4_B")
vectors.long

## Stream Flow is not significant. Everything else is. 

```

Making the plot.

```{r}

MB_RDA <- ggplot() + 
      geom_vline(xintercept = c(0), color = "grey70", linetype = 2) +
      geom_hline(yintercept = c(0), color = "grey70", linetype = 2) +  
      xlab(axis.long[1, "label"]) +
      ylab(axis.long[2, "label"]) +  
      scale_x_continuous(sec.axis = dup_axis(labels=NULL, name=NULL)) +
      scale_y_continuous(sec.axis = dup_axis(labels=NULL, name=NULL)) +    
      geom_point(data=sites.long, 
                 aes(x=axis1, y=axis2), 
                 size=1) +
      #geom_point(data=species.long_filt, 
      #          aes(x=axis1, y=axis2), size=1.5, color="dodgerblue3", alpha=0.6) +
      geom_text_repel(data=species.long, 
                    aes(x=axis1*1, y=axis2*1, label=labels),
                    color="dodgerblue4", size=2) +
      geom_segment(data=vectors.long,
                 aes(x=0, y=0, xend=axis1*1, yend=axis2*1), 
                 colour="black", size=0.5, arrow=arrow(type="open", length=unit(0.15, "cm"))) +
      geom_text_repel(data=vectors.long, 
                    aes(x=axis1*1, y=axis2*1, label=vector),
                    size=2,
                    colour="black") +
      ggsci::scale_colour_npg() +
      theme_classic() +
      coord_fixed(ratio=1) +
  ggtitle("A")


```

### St. Albans Bay. 
```{r}

## selecting phytoplankton that are > 5%

SA_Phyto_Date <- Phytos %>%
  filter(Station == "SA") %>%
  select(SampleDate) %>%
  unique()
  
SA_Phyto_Keep <- Phytos %>%
  filter(Station == "SA") %>%
  group_by(Sample_ID, SampleDate, Genus) %>%
  summarize(RA_BM = sum(RA_BM)) %>%
  mutate(Keep = if_else(RA_BM >= 0.05, "Yes", "No")) %>%
  ungroup() %>%
  select(Genus, Keep) %>%
  filter(Keep=="Yes") %>%
  unique()

SA_Phyto_Matrix <- Phytos %>%
  filter(Taxonomic_group == "Cyanobacteria") %>%
  filter(Station == "SA") %>%
  filter(Genus %in% SA_Phyto_Keep$Genus) %>%
  select(SampleDate, Genus, BM_ug.L) %>%
  group_by(SampleDate, Genus) %>%
  summarise(BM = sum(BM_ug.L)) %>%
  pivot_wider(names_from = "Genus", values_from="BM") %>%
  filter(SampleDate > as.Date("2021-06-01")) %>%
  rename(Date = SampleDate)

SA_Phyto_Matrix[is.na(SA_Phyto_Matrix)] <- 0

SA_Seston_Matrix <- All_Combined %>%
  select(SestonP_uML, SestonC_uML, SestonN_uML, Station, Date) %>%
  filter(Station == "SA") %>%
  unique() %>%
  mutate(Seston_CP = SestonC_uML/SestonP_uML,
         Seston_CN = SestonC_uML/SestonN_uML, 
         Seston_NP = SestonN_uML/SestonP_uML) %>%
  na.omit() %>%
  select(-SestonP_uML, -SestonC_uML, -SestonN_uML, -Station) %>%
  mutate(Date = ymd(Date)) %>%
    filter(Date %in% SA_Phyto_Date$SampleDate)

## Weather Matrix

SA_Wind_RDA <- SA_Met %>%
  mutate(Day = day(Datetime)) %>%
  mutate(Date = make_date(Year, Month, Day)) %>%
  select(Wind_Speed_m.s, Date) %>%
  filter(Date %in% SA_Phyto_Date$SampleDate) %>%
  group_by(Date) %>%
  summarize(Wind_Speed = mean(Wind_Speed_m.s))

SA_SS_RDA <- SA_Schmidt %>%
  mutate(Day = day(datetime),
         Month = month(datetime),
         Year = year(datetime),
         Date = make_date(Year, Month, Day)) %>%
  select(SS, Date) %>%
  filter(Date %in% SA_Phyto_Date$SampleDate) %>%
  group_by(Date) %>%
  summarize(SS = mean(SS))


# Water Temp

SA_WT_RDA <- SA_Profiler %>%
  mutate(Day = day(datetime),
         Month = month(datetime),
         Year = year(datetime),
         Date = make_date(Year, Month, Day)) %>%
  select(Temp_C, Date) %>%
  filter(Date %in% SA_Phyto_Date$SampleDate) %>%
  group_by(Date) %>%
  summarize(Temp_C = mean(Temp_C))

# Sum Stream Flow
SA_SF_RDA <- SA_SF_Stats %>%
  select(Sum_SF, Date) %>%
  filter(Date %in% SA_Phyto_Date$SampleDate) %>%
  group_by(Date) %>%
  summarize(Sum_SF = mean(Sum_SF)) 

## Dissolved Nutrients. 

DissNut_S <- read_xlsx("./DissolvedNutrients_2021.xlsx") %>%
  filter(site != "Miss Bay") %>%
  select(site, depth, rep, date, `NO3_mg/L`, `NH4_mg/L`, `PO4_mg/L`) %>%
  mutate(Date = ymd(date),
        depth = if_else(depth == "surface", "Surface", depth),
        depth = if_else(depth == "bottom", "Bottom", depth)) %>%
  mutate(NO3 = if_else(`NO3_mg/L` < 0, 0, `NO3_mg/L`),
         NH4 = if_else(`NH4_mg/L`< 0, 0, `NH4_mg/L`),
         PO4 = if_else(`PO4_mg/L` < 0, 0, `PO4_mg/L`),
         NO3 = NO3 * 1000,
         NH4 = NH4 * 1000,
         PO4 = PO4 * 1000,
         DIN = NO3 + NH4) %>%
    na.omit() %>%
  group_by(site, depth, Date) %>%
  filter(depth=="Surface") %>%
  summarize(NH4 = mean(NH4),
            NO3 = mean(NO3),
            PO4_S = mean(PO4),
            DIN_S = mean(DIN)) %>%
  ungroup() %>%
  select(DIN_S, PO4_S, Date)

DissNut_B <- read_xlsx("./DissolvedNutrients_2021.xlsx") %>%
  filter(site != "Miss Bay") %>%
  select(site, depth, rep, date, `NO3_mg/L`, `NH4_mg/L`, `PO4_mg/L`) %>%
  mutate(Date = ymd(date),
        depth = if_else(depth == "surface", "Surface", depth),
        depth = if_else(depth == "bottom", "Bottom", depth)) %>%
  mutate(NO3 = if_else(`NO3_mg/L` < 0, 0, `NO3_mg/L`),
         NH4 = if_else(`NH4_mg/L`< 0, 0, `NH4_mg/L`),
         PO4 = if_else(`PO4_mg/L` < 0, 0, `PO4_mg/L`),
         NO3 = NO3 * 1000,
         NH4 = NH4 * 1000,
         PO4 = PO4 * 1000,
         DIN = NO3 + NH4) %>%
    na.omit() %>%
  group_by(site, depth, Date) %>%
  filter(depth=="Bottom") %>%
  summarize(NH4 = mean(NH4),
            NO3 = mean(NO3),
            PO4_B = mean(PO4),
            DIN_B = mean(DIN)) %>%
  ungroup() %>%
  select(DIN_B, PO4_B, Date)
## Join together. 
  
SA_Env_RDA <- full_join(SA_SF_RDA, SA_Wind_RDA) %>%
  full_join(., SA_WT_RDA) %>%
  full_join(., SA_SS_RDA) %>%
  full_join(., DissNut_S) %>%
  full_join(., DissNut_B) %>%
  #full_join(., MB_Seston_Matrix) %>%
  na.omit()


SA_Phyto_RDA <- SA_Phyto_Matrix %>%
  filter(Date %in% SA_Env_RDA$Date) %>%
  column_to_rownames(var="Date")

SA_Phyto_RDA[is.na(SA_Phyto_RDA)] <- 0


SA_Env_RDA <-   SA_Env_RDA %>%
  rownames_to_column(var="Remove") %>%
  select(-Remove) %>%
  column_to_rownames(var="Date")
```

## Checking for Colinearity in Variables: 

```{r}

library(corrplot)

SA_Corr = cor(SA_Env_RDA)
corrplot(SA_Corr, method = 'number')

corrplot::cor

```


## Run RDA. 

```{r}
library(BiodiversityR)

SA_Phyto_RDA <- SA_Phyto_RDA %>%
  decostand("hellinger")

SA_Env_RDA <- SA_Env_RDA %>%
  decostand("standardize")


SA_dbrda <- dbrda(SA_Phyto_RDA ~ .,
                    data = SA_Env_RDA,
                  distance="bray")

print(SA_dbrda)

anova.cca(SA_dbrda)

```


Forward selection of the RDA


```{r}
# Initial RDA with ALL of the environmental data
SA_full <- dbrda(SA_Phyto_RDA ~ .,
                    data = SA_Env_RDA, 
                 distance="bray")

SA_null <- dbrda(SA_Phyto_RDA ~ 1, data=SA_Env_RDA, 
                 distance="bray")

modAIC <- MASS::stepAIC(SA_null,direction='forward', scope = list(lower = SA_null,
                                                              upper = SA_full))


SA_mod <- dbrda(SA_Phyto_RDA ~ DIN_S + DIN_B + Wind_Speed + Temp_C + PO4_S + 
    SS + Sum_SF, 
                data=SA_Env_RDA, distance="bray")

print(SA_mod)

anova.cca(SA_mod)

```


```{r}
library(BiodiversityR)

SA_mod_summary <- summary(SA_mod)

SA_mod_summary$concont

```


```{r}

## This code adds species scores back into the dbrda, since they are always missing. That way we can plot species on our ordination plot with the sites and environmental variables. 

sppscores(SA_mod) <- SA_Phyto_RDA

plot <- ordiplot(SA_mod, type = "point")

```


```{r}
# This code chunk extracts data from the dbRDA

sites.long <- sites.long(plot, env.data=SA_Env_RDA)

axis.long <- axis.long(SA_mod, choices=c(1, 2))


## Edit the species.long dataframe to include a column with abundance, then order abundance, and filter out....keep the top 10 functional groups. 

df <- colSums(SA_Phyto_RDA) %>%
  as.data.frame() %>%
  mutate(`.` = abs(`.`))

## Find Top 10 Functional Groups. 

species.long <- species.long(plot)
species.long


vectors.envfit <- envfit(plot, env=SA_Env_RDA)
vectors.long <- vectorfit.long(vectors.envfit)
vectors.long

## Stream Flow is not significant. Everything else is. 

```

Making the plot.

```{r}


SA_RDA <- ggplot() + 
      geom_vline(xintercept = c(0), color = "grey70", linetype = 2) +
      geom_hline(yintercept = c(0), color = "grey70", linetype = 2) +  
      xlab(axis.long[1, "label"]) +
      ylab(axis.long[2, "label"]) +  
      scale_x_continuous(sec.axis = dup_axis(labels=NULL, name=NULL)) +
      scale_y_continuous(sec.axis = dup_axis(labels=NULL, name=NULL)) +    
      geom_point(data=sites.long, 
                 aes(x=axis1, y=axis2), 
                 size=1) +
      #geom_point(data=species.long_filt, 
      #          aes(x=axis1, y=axis2), size=1.5, color="dodgerblue3", alpha=0.6) +
      geom_text_repel(data=species.long, 
                    aes(x=axis1*1, y=axis2*1, label=labels),
                    color="dodgerblue4", size=2) +
      geom_segment(data=vectors.long,
                 aes(x=0, y=0, xend=axis1*1, yend=axis2*1), 
                 colour="black", size=0.5, arrow=arrow(type="open", length=unit(0.15, "cm"))) +
      geom_text_repel(data=vectors.long, 
                    aes(x=axis1*1, y=axis2*1, label=vector),
                    size=2,
                    colour="black") +
      ggsci::scale_colour_npg() +
      theme_classic() +
      coord_fixed(ratio=1) +
  ggtitle("B")


```

################################################################################
# Dissolved Nutrient Analysis Figures

Now I am going to make similar figures as shown in the seston nutrient limitation figures, to corroborate the story with the dissolved nutrients.

To do so, we need to join the Dissolved Nutrients with Total Nutrients and Toxins. 

1. Rerun reading and cleaning the data in the CNP Analaysis Clean Sheet
2. Join Separate Dataframes here
3. Make each Figure
4. Print the figure in the Second Analysis Figs R. Sheet.

Dataframes: 
- Toxins
- Water_TNTP

```{r}
DissNut <- read_xlsx("./DissolvedNutrients_2021.xlsx") %>%
  select(site, depth, rep, date, `NO3_mg/L`, `NH4_mg/L`, `PO4_mg/L`) %>%
  mutate(date = ymd(date),
        depth = if_else(depth == "surface", "Surface", depth),
        depth = if_else(depth == "bottom", "Bottom", depth)) %>%
  mutate(NO3 = if_else(`NO3_mg/L` < 0, 0, `NO3_mg/L`),
         NH4 = if_else(`NH4_mg/L`< 0, 0, `NH4_mg/L`),
         PO4 = if_else(`PO4_mg/L` < 0, 0, `PO4_mg/L`),
         NO3 = NO3 * 1000,
         NH4 = NH4 * 1000,
         PO4 = PO4 * 1000,
         DIN = NO3 + NH4) %>%
    na.omit() %>%
  group_by(site, depth, date) %>%
  summarize(NH4 = mean(NH4),
            NO3 = mean(NO3),
            PO4 = mean(PO4),
            DIN = mean(DIN))

Water_TNTP <- read_csv("./LG21_Summer_TN-TP_BREE_Clean.csv") %>%
  mutate(site = if_else(Site == "Miss Bay", "Miss Bay", "STA Inner"),
         date = mdy(Date),
         depth = if_else(Location == "surface", "Surface", "Bottom")) %>%
 # filter(`TP_(uMol/L)` < 13 & `TP_(uMol/L)` > 0) %>%
  group_by(date, site, depth) %>%
  summarize(Water_TN_uML= mean(`TN_(uMol/L)`),
            Water_TP_uML = mean(`TP_(uMol/L)`),
            Water_TN_mgL = mean(`TN_mg/L`), 
            Water_TP_mgL = mean(`TP_mg/L`),
            TN = Water_TN_mgL * 1000,
            TP = Water_TP_mgL * 1000)


Nut <- full_join(DissNut, Water_TNTP) %>%
  na.omit()

Toxins <- read.csv("Toxins_SAMB2021_Clean.csv") %>%
  mutate(Microcystin = if_else(is.na(Microcystin), 0, Microcystin),
         Anatoxin = if_else(is.na(Anatoxin), 0, Anatoxin),
         depth = "IWC") %>%
  select(-Cylindrospermopsin, -SampleID) %>%
  mutate(date = mdy(Date)) %>%
  mutate(site = if_else(Station == "MB", "Miss Bay", "STA Inner")) %>%
  mutate(Toxin = if_else(Microcystin > 0 & Anatoxin == 0, "MC", "None"), 
         Toxin = if_else(Anatoxin > 0 & Microcystin == 0, "ATX", Toxin),
         Toxin = if_else(Anatoxin > 0 & Microcystin > 0, "Both", Toxin)) %>%
  select(-Station, -Date, -Anatoxin, -Microcystin, -depth)

Nut_Toxins <- full_join(Nut, Toxins)

```
Dissolved nutrients are missing 7/22/21.

## Dissolved Nutrient Statistics

I need to add some statistics into the results section to compare the pre-bloom levels of DIN and PO4 between the bays to support my claim that the dissolved organic nitrogen is the important metric in determining bloom severity between these two systems. 

```{r}

DissNut_Stat <- DissNut %>%
  group_by(date, site) %>%
  summarise(DIN = mean(DIN),
            PO4 = mean(PO4)) %>%
  mutate(Stage = if_else(date <= as_date("2021-07-15") & site == "STA Inner", "Pre-Bloom", "None"),
         Stage = if_else(date > as_date("2021-07-15") & date <= as_date("2021-07-27") & site == "STA Inner", "Exponential Phase", Stage),
         Stage = if_else(date > as_date("2021-07-27") & date <= as_date("2021-08-16") & site == "STA Inner", "Peak Growth", Stage),
         Stage = if_else(date > as_date("2021-08-16") & date <= as_date("2021-08-27") & site == "STA Inner", "Bloom Collapse ", Stage),
         Stage = if_else(date > as_date("2021-08-27") & site == "STA Inner", "Post-Bloom", Stage)) %>%
  mutate(Stage = if_else(date <= as_date("2021-08-07") & site == "Miss Bay", "Pre-Bloom", Stage),
         Stage = if_else(date > as_date("2021-08-07") & date <= as_date("2021-08-12") & site == "Miss Bay", "Exponential Phase 1", Stage),
         Stage = if_else(date > as_date("2021-08-12") & date <= as_date("2021-08-20") & site == "Miss Bay", "Peak Growth 1", Stage),
         Stage = if_else(date > as_date("2021-08-20") & date <= as_date("2021-08-24") & site == "Miss Bay", "Bloom Collapse 1", Stage),
         Stage = if_else(date > as_date("2021-08-24") & date <= as_date("2021-09-03") & site == "Miss Bay", "Exponential Phase 2", Stage),
         Stage = if_else(date > as_date("2021-09-03") & date <= as_date("2021-09-15") & site == "Miss Bay", "Peak Growth 2", Stage),
         Stage = if_else(date > as_date("2021-09-15") & date <= as_date("2021-09-27") & site == "Miss Bay", "Bloom Collapse 2", Stage),
         Stage = if_else(date > as_date("2021-09-27") & site == "Miss Bay", "Post-Bloom", Stage)) 



DissNut_Stat%>%  
  group_by(Stage, site) %>%
  summarise(Avg = mean(DIN),
            sd = sd(DIN),
            max = max(DIN))


DissNut_Stat%>%  
  group_by(Stage, site) %>%
  summarise(Avg = mean(PO4),
            sd = sd(PO4),
            max = max(PO4))


## 6/20-6/23 Dissolved nutrient data: 


```


Go ahead and make the figures now. 

Again, the requirements for limitation are: 

## Qualifications for N Limitation: 
# DIN < 100ug/L and DIN:TP < 1.6

## Qualifications for P limitation: 
# DIP < 10ug/L and DIN:TP >= 1.6


Dissolved Nitrogen: 
```{r}
DN_DIN <- Nut_Toxins %>%
  filter(depth == "Surface") %>%
  ggplot(aes(x=as.Date(date), y=DIN)) +
  annotate("text", x = as.Date("2021-06-07"), y = 1500, label = "N-Replete", size = 1.5, color="dodgerblue4") +
  annotate("text", x = as.Date("2021-06-07"), y = -50, label = "N-Deplete", size = 1.5, color="indianred4") +
  geom_hline(yintercept = 100, linetype=3, color="black", linewidth=0.25) +
  geom_line(aes(linetype=site)) +
  geom_point(aes(color=Toxin), size=0.75) +
  scale_color_manual(values=c("orangered3", "darkmagenta", "dodgerblue3", "black")) +
  theme_classic() +
  ylab("Dissolved Inorganic Nitrogen (ug/L)") +
  xlab("Date") +
  ggtitle("D") +
  ylim(-50,1500)+
  theme(axis.title = element_text(size=7), axis.text=element_text(size=6),
        plot.title = element_text(size=7), 
        legend.position="bottom",
        legend.title = element_text(size = 7), 
        legend.key.size = unit(0.05, 'in'), legend.text = element_text(size=6))+
  scale_x_date(breaks = scales::breaks_pretty(6), limits = c(as.Date("2021-06-01"), as.Date("2021-10-31")))

```

Dissolved Phosphorus: 
```{r}
DN_DIP <- Nut_Toxins %>%
  filter(depth == "Surface") %>%
  ggplot(aes(x=as.Date(date), y=PO4)) +
  annotate("text", x = as.Date("2021-06-07"), y = 20, label = "P-Replete", size = 1.5, color="dodgerblue4") +
  annotate("text", x = as.Date("2021-06-07"), y = 9.5, label = "P-Deplete", size = 1.5, color="indianred4") +
  geom_hline(yintercept = 10, linetype=3, color="black", linewidth=0.25) +
  geom_line(aes(linetype=site)) +
  geom_point(aes(color=Toxin), size=0.75) +
  scale_color_manual(values=c("orangered3", "darkmagenta", "dodgerblue3", "black")) +
  theme_classic() +
  ylab("Dissolved Inorganic Phosphorus (ug/L)") +
  xlab("Date") +
  ylim(0,20)+
  ggtitle("E")
  theme(axis.title = element_text(size=7), axis.text=element_text(size=6),
        plot.title = element_text(size=7), 
        legend.position="bottom",
        legend.title = element_text(size = 7), 
        legend.key.size = unit(0.05, 'in'), legend.text = element_text(size=6))+
  scale_x_date(breaks = scales::breaks_pretty(6), limits = c(as.Date("2021-06-01"), as.Date("2021-10-31")))

```

DIN/TP Ratios: 
```{r}

DN_DIN.TP <- Nut_Toxins %>%
  filter(depth == "Surface") %>%
  mutate(DIN.TP = DIN/TP) %>%
  ggplot(aes(x=as.Date(date), y=DIN.TP)) +
  annotate("text", x = as.Date("2021-06-07"), y = 140, label = "P-Deplete", size = 1.5, color="indianred4") +
  annotate("text", x = as.Date("2021-06-07"), y = 0.5, label = "N-Deplete", size = 1.5, color="indianred4") +
  geom_hline(yintercept = 1.6, linetype=3, color="black", linewidth=0.25) +
  geom_line(aes(linetype=site)) +
  geom_point(aes(color=Toxin), size=0.75) +
  scale_color_manual(values=c("orangered3", "darkmagenta", "dodgerblue3", "black")) +
  theme_classic() +
  ylab("DIN:TP") +
  xlab("Date") +
  ggtitle("F")+
  ylim(0,105)+
  theme(axis.title = element_text(size=7), axis.text=element_text(size=6),
        plot.title = element_text(size=7), 
        legend.position="bottom",
        legend.title = element_text(size = 7), 
        legend.key.size = unit(0.05, 'in'), legend.text = element_text(size=6))+
   scale_y_continuous(trans='log2', limits = c(0.3, 150), breaks=c(0.5, 1, 1.6, 5, 10, 25, 50, 100)) +
  scale_x_date(breaks = scales::breaks_pretty(6), limits = c(as.Date("2021-06-01"), as.Date("2021-10-31")))


```

## Bottom Nutrients: 

Dissolved Nitrogen: 
```{r}
DN_DIN_B <- Nut_Toxins %>%
  filter(depth == "Bottom") %>%
  ggplot(aes(x=as.Date(date), y=DIN)) +
  annotate("text", x = as.Date("2021-06-07"), y = 2000, label = "N-Replete", size = 1.5, color="dodgerblue4") +
  annotate("text", x = as.Date("2021-06-07"), y = -50, label = "N-Deplete", size = 1.5, color="indianred4") +
  geom_hline(yintercept = 100, linetype=3, color="black", linewidth=0.25) +
  geom_line(aes(linetype=site)) +
  geom_point(aes(color=Toxin), size=0.75) +
  scale_color_manual(values=c("orangered3", "darkmagenta", "dodgerblue3", "black")) +
  theme_classic() +
  ylab("Dissolved Inorganic Nitrogen (ug/L)") +
  xlab("") +
  ylim(-50,2000)+
  theme(axis.title = element_text(size=7), axis.text=element_text(size=6),
        plot.title = element_text(size=7), 
        legend.position="bottom",
        legend.title = element_text(size = 7), 
        legend.key.size = unit(0.05, 'in'), legend.text = element_text(size=6))+
  scale_x_date(breaks = scales::breaks_pretty(6), limits = c(as.Date("2021-06-01"), as.Date("2021-10-31")))

```

Dissolved Phosphorus: 
```{r}
DN_DIP_B <- Nut_Toxins %>%
  filter(depth == "Bottom") %>%
  ggplot(aes(x=as.Date(date), y=PO4)) +
  annotate("text", x = as.Date("2021-06-07"), y = 12, label = "P-Replete", size = 1.5, color="dodgerblue4") +
  annotate("text", x = as.Date("2021-06-07"), y = 9.5, label = "P-Deplete", size = 1.5, color="indianred4") +
  geom_hline(yintercept = 10, linetype=3, color="black", linewidth=0.25) +
  geom_line(aes(linetype=site)) +
  geom_point(aes(color=Toxin), size=0.75) +
  scale_color_manual(values=c("orangered3", "darkmagenta", "dodgerblue3", "black")) +
  theme_classic() +
  ylab("Dissolved Inorganic Phosphorus (ug/L)") +
  xlab("") +
  ylim(0,12)+
  theme(axis.title = element_text(size=7), axis.text=element_text(size=6),
        plot.title = element_text(size=7), 
        legend.position="bottom",
        legend.title = element_text(size = 7), 
        legend.key.size = unit(0.05, 'in'), legend.text = element_text(size=6))+
  scale_x_date(breaks = scales::breaks_pretty(6), limits = c(as.Date("2021-06-01"), as.Date("2021-10-31")))

```

DIN/TP Ratios: 
```{r}

DN_DIN.TP_B <- Nut_Toxins %>%
  filter(depth == "Bottom") %>%
  mutate(DIN.TP = DIN/TP) %>%
  ggplot(aes(x=as.Date(date), y=DIN.TP)) +
  annotate("text", x = as.Date("2021-06-07"), y = 75, label = "P-Deplete", size = 1.5, color="indianred4") +
  annotate("text", x = as.Date("2021-06-07"), y = 0.5, label = "N-Deplete", size = 1.5, color="indianred4") +
  geom_hline(yintercept = 1.6, linetype=3, color="black", linewidth=0.25) +
  geom_line(aes(linetype=site)) +
  geom_point(aes(color=Toxin), size=0.75) +
  scale_color_manual(values=c("orangered3", "darkmagenta", "dodgerblue3", "black")) +
  theme_classic() +
  ylab("DIN:TP") +
  xlab("Date") +
  ylim(0,105)+
  theme(axis.title = element_text(size=7), axis.text=element_text(size=6),
        plot.title = element_text(size=7), 
        legend.position="bottom",
        legend.title = element_text(size = 7), 
        legend.key.size = unit(0.05, 'in'), legend.text = element_text(size=6))+
  scale_y_continuous(trans='log2', limits = c(0.1, 75), breaks=c(0.1, 0.5, 1, 1.6, 5, 10, 25, 75)) +
  scale_x_date(breaks = scales::breaks_pretty(6), limits = c(as.Date("2021-06-01"), as.Date("2021-10-31")))


```



I want to update these to match the total nutrients figures from the supplemental information. That way we can see the bottom and top nutrients together. 


```{r}

DN_DIN <- Nut_Toxins %>%
  ggplot() +
  annotate("text", x = as.Date("2021-06-07"), y = 2000, label = "N-Replete", size = 1.5, color="dodgerblue4") +
  annotate("text", x = as.Date("2021-06-07"), y = 3, label = "N-Deplete", size = 1.5, color="indianred4") +
  geom_hline(yintercept = 100, linetype=3, color="black", linewidth=0.25) +
  geom_line(aes(x = as.Date(date), y = DIN, linetype=site, group = interaction(depth, site)), size = 0.5) + 
  geom_point(aes(x = as.Date(date), y = DIN,  shape=depth, fill=Toxin, color=Toxin, group= interaction(depth, site)), size=0.75) +
  scale_shape_manual(values=c(21, 22))+
  scale_fill_manual(values=c("orangered3", "darkmagenta", "dodgerblue3", "black", "grey")) +
  scale_color_manual(values=c("orangered3", "darkmagenta", "dodgerblue3", "black", "grey")) +
  theme_classic() +
  ylab(expression(paste("DIN (",~ mu, "g/L)"))) +
  xlab("") +
  ggtitle("D")+
  theme(axis.title = element_text(size=7), axis.text=element_text(size=6),
        plot.title = element_text(size=7), 
        legend.position="bottom",
        legend.title = element_text(size = 7), 
        legend.key.size = unit(0.05, 'in'), legend.text = element_text(size=6),
       plot.margin = unit(c(0, 0.05, 0, 0.05), 'in'))+
    scale_y_continuous(trans='log2', limits = c(3, 2000), breaks=c(3, 25, 50, 100, 250, 500, 1000, 2000)) +
  scale_x_date(breaks = scales::breaks_pretty(6), limits = c(as.Date("2021-06-01"), as.Date("2021-10-31")))


DN_PO4 <- Nut_Toxins %>%
  ggplot() +
  annotate("text", x = as.Date("2021-06-07"), y = 20, label = "P-Replete", size = 1.5, color="dodgerblue4") +
  annotate("text", x = as.Date("2021-06-07"), y = 8, label = "P-Deplete", size = 1.5, color="indianred4") +
  geom_hline(yintercept = 10, linetype=3, color="black", linewidth=0.25) +
  geom_line(aes(x = as.Date(date), y = PO4, linetype=site, group = interaction(depth, site)), size = 0.5) + 
  geom_point(aes(x = as.Date(date), y = PO4,  shape=depth, fill=Toxin, color=Toxin, group= interaction(depth, site)), size=0.75) +
  scale_shape_manual(values=c(21, 22))+
  scale_fill_manual(values=c("orangered3", "darkmagenta", "dodgerblue3", "black", "grey")) +
  scale_color_manual(values=c("orangered3", "darkmagenta", "dodgerblue3", "black", "grey")) +
  theme_classic() +
  ylab(expression(paste("PO4 (",~ mu, "g/L)"))) +
  xlab("") +
  ggtitle("E")+
  ylim(0,20)+
  theme(axis.title = element_text(size=7), axis.text=element_text(size=6),
        plot.title = element_text(size=7), 
        legend.position="bottom",
        legend.title = element_text(size = 7), 
        legend.key.size = unit(0.05, 'in'), legend.text = element_text(size=6),
       plot.margin = unit(c(0, 0.05, 0, 0.05), 'in'))+
  scale_y_continuous(trans='log2', limits = c(0.1, 20), breaks=c(0.1, 0.5, 1, 2, 3, 4, 5, 10, 20)) +
  scale_x_date(breaks = scales::breaks_pretty(6), limits = c(as.Date("2021-06-01"), as.Date("2021-10-31")))


DN_DIN.TP <- Nut_Toxins %>%
  mutate(DIN.TP = DIN/TP) %>%
  ggplot() +
  annotate("text", x = as.Date("2021-06-07"), y = 75, label = "P-Deplete", size = 1.5, color="indianred4") +
  annotate("text", x = as.Date("2021-06-07"), y = 0.5, label = "N-Deplete", size = 1.5, color="indianred4") +
  geom_hline(yintercept = 1.6, linetype=3, color="black", linewidth=0.25) +
  geom_line(aes(x = as.Date(date), y = DIN.TP, linetype=site, group = interaction(depth, site)), size = 0.5) + 
  geom_point(aes(x = as.Date(date), y = DIN.TP,  shape=depth, fill=Toxin, color=Toxin, group= interaction(depth, site)), size=0.75) +
  scale_shape_manual(values=c(21, 22))+
  scale_fill_manual(values=c("orangered3", "darkmagenta", "dodgerblue3", "black", "grey")) +
  scale_color_manual(values=c("orangered3", "darkmagenta", "dodgerblue3", "black", "grey")) +
  theme_classic() +
  ylab("DIN:TP") +
  xlab("") +
  ggtitle("F")+
  ylim(0,105)+
 theme(axis.title = element_text(size=7), axis.text=element_text(size=6),
        plot.title = element_text(size=7), 
        legend.position="bottom",
        legend.title = element_text(size = 7), 
        legend.key.size = unit(0.05, 'in'), legend.text = element_text(size=6),
        plot.margin = unit(c(0, 0.05, 0, 0.05), 'in'))+
  scale_y_continuous(trans='log2', limits = c(0.1, 75), breaks=c(0.1, 0.5, 1, 1.6, 5, 10, 25, 75)) +
  scale_x_date(breaks = scales::breaks_pretty(6), limits = c(as.Date("2021-06-01"), as.Date("2021-10-31")))

```
# Addressing Collaborator Questions: 

When did each bay hit 21 C? Did one bay warm up faster than another?

```{r}
MB_Profiler %>%
  filter(Depth == 0.5 | Depth == 1.0) %>%
  filter(Temp_C >= 25)


SA_Profiler %>%
  filter(Depth == 0.5 | Depth == 1.0) %>%
  filter(Temp_C >= 25)
```



Running Citations for R Packages: 

```{r}
citation("MASS")
citation("stats")
citation("factoextra")
citation("rLakeAnalyzer")

```

