---
title: "Descriptive Statistics"
author: "Katelynn"
date: "2024-10-14"
output: html_document
---

# Descriptive Statistics for Manuscript Results


### Water Temperature

```{r}
SA_Temp_Stats1 <- SA_Profiler %>%
  select(Depth, datetime, Temp_C, Month, Day, Year, Group) %>%
  mutate(Site = "SA") %>%
  filter(Depth == 1.0) %>%
  group_by(Depth, datetime, Site) %>%
  summarize(Temp_C = mean(Temp_C))


MB_Temp_Stats1 <- MB_Profiler %>%
  select(Depth, datetime, Temp_C, Month, Day, Year, Group) %>%
  mutate(Site = "MB") %>%
  filter(Depth == 1.0) %>%
  group_by(Depth, datetime, Site) %>%
  rename(Depth = Depth) %>%
  summarize(Temp_C = mean(Temp_C))

Temp_Stats_1 <- inner_join(SA_Temp_Stats1, MB_Temp_Stats1, by="datetime") %>%
  na.omit()

SA_Stats_1 <- Temp_Stats_1 %>%
  select(datetime, Site.x, Temp_C.x) %>%
  rename(Site = Site.x, 
         Temp_C = Temp_C.x)

MB_Stats_1 <- Temp_Stats_1 %>%
  select(datetime, Site.y, Temp_C.y) %>%
  rename(Site = Site.y, 
         Temp_C = Temp_C.y)

Temp_Stats_1 <- bind_rows(SA_Stats_1, MB_Stats_1) %>%
  na.omit()


### Normality: 

shapiro.test(SA_Stats_1$Temp_C)

shapiro.test(MB_Stats_1$Temp_C)


# Paired Samples Wilcoxon Test
result = wilcox.test(Temp_C ~ Site,
                    data = Temp_Stats_1,
                    paired = FALSE,
                    alternative = "two.sided")

# Printing the results
print(result)




Temp_Stats_1 %>%
  group_by(Site) %>%
  summarise(Avg = mean(Temp_C),
            sd = sd(Temp_C))

### Bottom Water Temperatures

SA_Temp_StatsBot <- SA_Profiler %>%
  select(Depth, datetime, Temp_C, Month, Day, Year, Group) %>%
  mutate(Site = "SA") %>%
  filter(Depth == 4.5) %>%
  group_by(Depth, datetime, Site) %>%
  summarize(Temp_C = mean(Temp_C))


MB_Temp_StatsBot<- MB_Profiler %>%
  select(Depth, datetime, Temp_C, Month, Day, Year, Group) %>%
  mutate(Site = "MB") %>%
  filter(Depth == 2.5) %>%
  group_by(Depth, datetime, Site) %>%
  rename(Depth = Depth) %>%
  summarize(Temp_C = mean(Temp_C))

Temp_Stats_Bot <- inner_join(SA_Temp_StatsBot, MB_Temp_StatsBot, by="datetime") %>%
  na.omit()

SA_Stats_Bot <- Temp_Stats_Bot %>%
  select(datetime, Site.x, Temp_C.x) %>%
  rename(Site = Site.x, 
         Temp_C = Temp_C.x)

MB_Stats_Bot <- Temp_Stats_Bot %>%
  select(datetime, Site.y, Temp_C.y) %>%
  rename(Site = Site.y, 
         Temp_C = Temp_C.y)

Temp_Stats_Bot <- bind_rows(SA_Stats_Bot, MB_Stats_Bot) %>%
  na.omit()

### Normality: 

shapiro.test(SA_Stats_Bot$Temp_C)

shapiro.test(MB_Stats_Bot$Temp_C)



# Paired Samples Wilcoxon Test
result = wilcox.test(Temp_C ~ Site,
                    data = Temp_Stats_Bot,
                    paired = FALSE,
                    alternative = "two.sided")

# Printing the results
print(result)
4.035e-11*6

### Averages and sd

Temp_Stats_Bot %>%
  group_by(Site) %>%
  summarise(Avg = mean(Temp_C),
            sd = sd(Temp_C))



### Difference in water column temperatures. 

SA_Temp_Stats_Diff <- SA_Profiler %>%
  select(Depth, datetime, Temp_C, Month, Day, Year, Group) %>%
  mutate(Site = "SA") %>%
  filter(Depth == 1.0 | Depth == 4.5) %>%
  group_by(Depth, datetime, Site) %>%
  summarize(Temp_C = mean(Temp_C)) %>%
  pivot_wider(names_from = Depth, values_from = Temp_C) %>%
  mutate(Diff= `4.5`-`1`) %>%
  select(datetime, Diff, Site)


MB_Temp_Stats_Diff <- MB_Profiler %>%
  select(Depth, datetime, Temp_C, Month, Day, Year) %>%
  mutate(Site = "MB") %>%
  filter(Depth == 1.0 | Depth == 2.5) %>%
  group_by(Depth, datetime, Site) %>%
  rename(Depth = Depth) %>%
  summarize(Temp_C = mean(Temp_C)) %>%
  pivot_wider(names_from = Depth, values_from = Temp_C)  %>%
  mutate(Diff = `2.5`-`1`) %>%
  select(datetime, Diff, Site)


Temp_Stats_Diff <- inner_join(SA_Temp_Stats_Diff, MB_Temp_Stats_Diff, by="datetime") 

SA_Stats_Diff <- Temp_Stats_Diff %>%
  select(datetime, Site.x, Diff.x) %>%
  rename(Site = Site.x, 
         Diff = Diff.x)

MB_Stats_Diff <- Temp_Stats_Diff %>%
  select(datetime, Site.y, Diff.y) %>%
  rename(Site = Site.y, 
         Diff = Diff.y)

Temp_Stats_Diff <- bind_rows(SA_Temp_Stats_Diff, MB_Temp_Stats_Diff) %>%
  na.omit()


### Normality: 

shapiro.test(SA_Stats_Diff$Diff)

shapiro.test(MB_Stats_Diff$Diff)


# Paired Samples Wilcoxon Test
result = wilcox.test(Diff ~ Site,
                    data = Temp_Stats_Diff,
                    paired = FALSE,
                    alternative = "two.sided")

# Printing the results
print(result)

2.2e-16*6
Temp_Stats_Diff %>%
  group_by(Site) %>%
  summarise(Avg = mean(Diff),
            sd = sd(Diff))

```

### Wind Speed

```{r}
SA_Wind_Stats <- SA_Met %>%
  select(Datetime, Wind_Speed_m.s, Month, Year) %>%
  mutate(Day = day(Datetime)) %>%
  mutate(Date = make_date(Year, Month, Day)) %>%
  mutate(Site = "SA") %>%
  rename(Wind_Speed = Wind_Speed_m.s) %>%
  filter(Month>=6 & Month < 11) %>%
  mutate(Group = if_else(Date < as.Date("2021-09-30"), 1, 0),
         Group = if_else(Date >= as.Date("2021-10-11"), 2, Group)) %>%
  filter(Group != 0) %>%
  select(-Group, -Date, -Month, -Day, -Year)

MB_Wind_Stats <- MB_Met %>%
  select(Datetime, Wind_Speed, Month) %>%
  mutate(Site = "MB") %>%
  filter(Month>=6 & Month < 11) %>%
  select(-Month)

Wind_Stats <- bind_rows(MB_Wind_Stats, SA_Wind_Stats) %>%
  na.omit()

shapiro.test(MB_Wind_Stats$Wind_Speed)


# Paired Samples Wilcoxon Test
result = wilcox.test(Wind_Speed ~ Site,
                    data = Wind_Stats,
                    paired = FALSE,
                    alternative = "two.sided")

# Printing the results
print(result)
2.36e-05*6

Wind_Stats %>%
  group_by(Site) %>%
  summarise(Avg = mean(Wind_Speed),
            sd = sd(Wind_Speed))




```
## Bottom DO

```{r}

SA_DO_Stats <- SA_Profiler %>%
  filter(Depth == 4.5) %>%
  select(datetime, ODOmgL) %>%
  mutate(Site = "SA") 

MB_DO_Stats <- MB_Profiler %>%
  filter(Depth == 2.5) %>%
  select(datetime, ODOmgL) %>%
  mutate(Site = "MB") 


DO_Stats <- inner_join(SA_DO_Stats, MB_DO_Stats, by="datetime") %>%
  na.omit()

SA_DO_Stats <- DO_Stats %>%
  select(datetime, Site.x, ODOmgL.x) %>%
  rename(Site = Site.x, 
         DO = ODOmgL.x)

MB_DO_Stats <- DO_Stats %>%
  select(datetime, Site.y, ODOmgL.y) %>%
  rename(Site = Site.y, 
         DO = ODOmgL.y)

DO_Stats <- bind_rows(SA_DO_Stats, MB_DO_Stats) %>%
  na.omit()


shapiro.test(MB_DO_Stats$DO)
shapiro.test(SA_DO_Stats$DO)

# Paired Samples Wilcoxon Test
result = wilcox.test(DO ~ Site,
                    data = DO_Stats,
                    paired = FALSE,
                    alternative = "two.sided")

# Printing the results
print(result)
2.2e-16*7

DO_Stats %>%
  group_by(Site) %>%
  summarise(Avg = mean(DO),
            sd = sd(DO),
            max = max(DO),
            min = min(DO))


```


### Schmidt Stability

```{r}

SA_SS_Stats <- SA_Schmidt %>%
  select(datetime, SS) %>%
  mutate(Site = "SA") %>%
  mutate(SS = if_else(SS < 0, 0, SS))

MB_SS_Stats <- MB_Schmidt %>%
  select(datetime, SS) %>%
  mutate(Site = "MB") %>%
  mutate(SS = if_else(SS < 0, 0, SS))


SS_Stats <- inner_join(SA_SS_Stats, MB_SS_Stats, by="datetime") %>%
  na.omit()

SA_SS_Stats <- SS_Stats %>%
  select(datetime, Site.x, SS.x) %>%
  rename(Site = Site.x, 
         SS = SS.x)

MB_SS_Stats <- SS_Stats %>%
  select(datetime, Site.y, SS.y) %>%
  rename(Site = Site.y, 
         SS = SS.y)

SS_Stats <- bind_rows(SA_SS_Stats, MB_SS_Stats) %>%
  na.omit()


shapiro.test(MB_SS_Stats$SS)
shapiro.test(SA_SS_Stats$SS)

# Paired Samples Wilcoxon Test
result = wilcox.test(SS ~ Site,
                    data = SS_Stats,
                    paired = FALSE,
                    alternative = "two.sided")

# Printing the results
print(result)
2.2e-16*6

SS_Stats %>%
  group_by(Site) %>%
  summarise(Avg = mean(SS),
            sd = sd(SS),
            max = max(SS))

```

### Stream Flow

```{r}

SA_SF_Stats <- Precip_Data_SA  %>%
  select(Date, Sum_SF) %>%
  mutate(Site = "SA")

MB_SF_Stats <- Precip_Data_MB  %>%
  select(Date, Sum_SF) %>%
  mutate(Site = "MB")

SF_Stats <- bind_rows(SA_SF_Stats, MB_SF_Stats) %>%
  na.omit()

shapiro.test(SA_SF_Stats$Sum_SF)
shapiro.test(MB_SF_Stats$Sum_SF)

# Paired Samples Wilcoxon Test
result = wilcox.test(Sum_SF ~ Site,
                    data = SF_Stats,
                    paired = FALSE,
                    alternative = "two.sided")

# Printing the results
print(result)
2.2e-16*4

SF_Stats %>%
  group_by(Site) %>%
  summarise(Avg = mean(Sum_SF),
            sd = sd(Sum_SF),
            max = max(Sum_SF))

```

## Bloom Stages Statistics:

Using the dates determined from hierarchal clustering below, we are going to create some statistics for the results section regarding trends in physical properties of the lake across bloom stages. 

Missisquoi Bay Dates:

2021-06-01 - 2021-08-07 pre bloom
2021-08-07 - 2021-08-12: Exponential Phase 1
2021-08-12 - 2021-08-20 : Peak Growth 1
2021-08-20 - 2021-08-24: Bloom Collapse 1
2021-08-24 - 2021-09-03 Exponential growth 2
2021-09-03 - 2021-09-15 Peak Growth 2
2021-09-15 - 2021-09-27 Bloom Collpase 2
2021-09-27 - 2021-10-31: Post-Bloom



```{r}

MB_Temp1_Stage <- MB_Temp_Stats1 %>%
  mutate(Stage = if_else(datetime <= as_datetime("2021-08-07 00:00:01"), "Pre-Bloom", "None"),
         Stage = if_else(datetime > as_datetime("2021-08-07 00:00:01") & datetime <= as_datetime("2021-08-12 00:00:01"), "Exponential Phase 1", Stage),
         Stage = if_else(datetime > as_datetime("2021-08-12 00:00:01") & datetime <= as_datetime("2021-08-20 00:00:01"), "Peak Growth 1", Stage),
         Stage = if_else(datetime > as_datetime("2021-08-20 00:00:01") & datetime <= as_datetime("2021-08-24 00:00:01"), "Bloom Collapse 1", Stage),
         Stage = if_else(datetime > as_datetime("2021-08-24 00:00:01") & datetime <= as_datetime("2021-09-03 00:00:01"), "Exponential Phase 2", Stage),
         Stage = if_else(datetime > as_datetime("2021-09-03 00:00:01") & datetime <= as_datetime("2021-09-15 00:00:01"), "Peak Growth 2", Stage),
         Stage = if_else(datetime > as_datetime("2021-09-15 00:00:01") & datetime <= as_datetime("2021-09-27 00:00:01"), "Bloom Collapse 2", Stage),
         Stage = if_else(datetime > as_datetime("2021-09-27 00:00:01"), "Post-Bloom", Stage)) 

MB_Temp1_Stage <- MB_Temp1_Stage %>%
  na.omit()

MB_Temp1_Stage <- MB_Temp1_Stage %>%
  mutate(Temp_log = log(Temp_C))

shapiro.test(MB_Temp1_Stage$Temp_log)

test <- kruskal.test(Temp_C~Stage, data=MB_Temp1_Stage)

print(test)

test <- dunn.test(MB_Temp1_Stage$Temp_C, MB_Temp1_Stage$Stage, method="bonferroni")
print(test)

MB_Temp1_Stage %>%  
  group_by(Stage) %>%
  summarise(Avg = mean(Temp_C),
            sd = sd(Temp_C),
            max = max(Temp_C))
  
###

MB_Schmidt_Stage <-  MB_Schmidt %>% 
  mutate(Stage = if_else(datetime <= as_datetime("2021-08-07 00:00:01"), "Pre-Bloom", "None"),
         Stage = if_else(datetime > as_datetime("2021-08-07 00:00:01") & datetime <= as_datetime("2021-08-12 00:00:01"), "Exponential Phase 1", Stage),
         Stage = if_else(datetime > as_datetime("2021-08-12 00:00:01") & datetime <= as_datetime("2021-08-20 00:00:01"), "Peak Growth 1", Stage),
         Stage = if_else(datetime > as_datetime("2021-08-20 00:00:01") & datetime <= as_datetime("2021-08-24 00:00:01"), "Bloom Collapse 1", Stage),
         Stage = if_else(datetime > as_datetime("2021-08-24 00:00:01") & datetime <= as_datetime("2021-09-03 00:00:01"), "Exponential Phase 2", Stage),
         Stage = if_else(datetime > as_datetime("2021-09-03 00:00:01") & datetime <= as_datetime("2021-09-15 00:00:01"), "Peak Growth 2", Stage),
         Stage = if_else(datetime > as_datetime("2021-09-15 00:00:01") & datetime <= as_datetime("2021-09-27 00:00:01"), "Bloom Collapse 2", Stage),
         Stage = if_else(datetime > as_datetime("2021-09-27 00:00:01"), "Post-Bloom", Stage)) 

MB_Schmidt_Stage <- MB_Schmidt_Stage %>%
  mutate(SS = if_else(SS < 0, 0, SS)) %>%
  na.omit()

shapiro.test(MB_Schmidt_Stage$SS)

test <- kruskal.test(SS~Stage, data=MB_Schmidt_Stage)

dunn.test(MB_Schmidt_Stage$SS, MB_Schmidt_Stage$Stage, method="bonferroni")


MB_Schmidt_Stage %>%  
  group_by(Stage) %>%
  summarise(Avg = mean(SS),
            sd = sd(SS),
            max = max(SS))
  

```
```{r}
###

MB_O2_Stage <-  MB_Profiler %>%
  filter(Depth == 2.5) %>%
  select(datetime, ODOmgL) %>%
  group_by(datetime) %>%
  summarize(ODOmgL = mean(ODOmgL)) %>%
  mutate(Stage = if_else(datetime <= as_datetime("2021-08-07 00:00:01"), "Pre-Bloom", "None"),
         Stage = if_else(datetime > as_datetime("2021-08-07 00:00:01") & datetime <= as_datetime("2021-08-12 00:00:01"), "Exponential Phase 1", Stage),
         Stage = if_else(datetime > as_datetime("2021-08-12 00:00:01") & datetime <= as_datetime("2021-08-20 00:00:01"), "Peak Growth 1", Stage),
         Stage = if_else(datetime > as_datetime("2021-08-20 00:00:01") & datetime <= as_datetime("2021-08-24 00:00:01"), "Bloom Collapse 1", Stage),
         Stage = if_else(datetime > as_datetime("2021-08-24 00:00:01") & datetime <= as_datetime("2021-09-03 00:00:01"), "Exponential Phase 2", Stage),
         Stage = if_else(datetime > as_datetime("2021-09-03 00:00:01") & datetime <= as_datetime("2021-09-15 00:00:01"), "Peak Growth 2", Stage),
         Stage = if_else(datetime > as_datetime("2021-09-15 00:00:01") & datetime <= as_datetime("2021-09-27 00:00:01"), "Bloom Collapse 2", Stage),
         Stage = if_else(datetime > as_datetime("2021-09-27 00:00:01"), "Post-Bloom", Stage)) 

shapiro.test(MB_O2_Stage$ODOmgL)

test <- kruskal.test(ODOmgL~Stage, data=MB_O2_Stage)

library(dunn.test)

dunn.test(MB_O2_Stage$ODOmgL, MB_O2_Stage$Stage, method="bonferroni")


MB_O2_Stage %>%  
  group_by(Stage) %>%
  summarise(Avg = mean(ODOmgL),
            sd = sd(ODOmgL),
            max = max(ODOmgL),
            min = min(ODOmgL))
  
  

```



St. Albans Bay 

St. Albans Dates: 

2021-06-01 - 2021-07-11: Pre-Bloom
2021-07-11 - 2021-07-15: Pre-Bloom, Bloom Collapse
2021-07-15 - 2021-07-27: Exponential Growth
2021-07-27 - 2021-08-16: Peak Growth
2021-08-16 - 2021-08-27: Bloom Collapse
2021-08-27 - 2021-10-31: Post-bloom

```{r}

SA_Temp1_Stage <- SA_Temp_Stats1 %>%
  mutate(Stage = if_else(datetime <= as_datetime("2021-07-15 00:00:01"), "Pre-Bloom", "None"),
         Stage = if_else(datetime > as_datetime("2021-07-15 00:00:01") & datetime <= as_datetime("2021-07-27 00:00:01"), "Exponential Phase", Stage),
         Stage = if_else(datetime > as_datetime("2021-07-27 00:00:01") & datetime <= as_datetime("2021-08-16 00:00:01"), "Peak Growth", Stage),
         Stage = if_else(datetime > as_datetime("2021-08-16 00:00:01") & datetime <= as_datetime("2021-08-27 00:00:01"), "Bloom Collapse ", Stage),
         Stage = if_else(datetime > as_datetime("2021-08-27 00:00:01"), "Post-Bloom", Stage)) 

SA_Temp1_Stage <- SA_Temp1_Stage %>%
  na.omit() %>%
  mutate(Temp_C_S = scale(Temp_C))


test <- kruskal.test(Temp_C~Stage, data=SA_Temp1_Stage)

print(test)

dunn.test(SA_Temp1_Stage$Temp_C, SA_Temp1_Stage$Stage, method="bonferroni")


SA_Temp1_Stage %>%  
  group_by(Stage) %>%
  summarise(Avg = mean(Temp_C),
            sd = sd(Temp_C),
            max = max(Temp_C))
  
###

SA_Schmidt_Stage <-  SA_Schmidt %>% 
  mutate(Stage = if_else(datetime <= as_datetime("2021-07-15 00:00:01"), "Pre-Bloom", "None"),
         Stage = if_else(datetime > as_datetime("2021-07-15 00:00:01") & datetime <= as_datetime("2021-07-27 00:00:01"), "Exponential Phase", Stage),
         Stage = if_else(datetime > as_datetime("2021-07-27 00:00:01") & datetime <= as_datetime("2021-08-16 00:00:01"), "Peak Growth", Stage),
         Stage = if_else(datetime > as_datetime("2021-08-16 00:00:01") & datetime <= as_datetime("2021-08-27 00:00:01"), "Bloom Collapse ", Stage),
         Stage = if_else(datetime > as_datetime("2021-08-27 00:00:01"), "Post-Bloom", Stage)) 

SA_Schmidt_Stage <- SA_Schmidt_Stage %>%
  mutate(SS = if_else(SS < 0, 0, SS)) %>%
  na.omit()

test <- kruskal.test(SS~Stage, data=SA_Schmidt_Stage)

print(test)

dunn.test(SA_Schmidt_Stage$SS, SA_Schmidt_Stage$Stage, method="bonferroni")



SA_Schmidt_Stage %>%  
  group_by(Stage) %>%
  summarise(Avg = mean(SS),
            sd = sd(SS),
            max = max(SS))
  

```

```{r}
###

SA_O2_Stage <-  SA_Profiler %>%
  filter(Depth == 4.5) %>%
  select(datetime, ODOmgL) %>%
  group_by(datetime) %>%
  summarize(ODOmgL = mean(ODOmgL)) %>%
  mutate(Stage = if_else(datetime <= as_datetime("2021-07-15 00:00:01"), "Pre-Bloom", "None"),
         Stage = if_else(datetime > as_datetime("2021-07-15 00:00:01") & datetime <= as_datetime("2021-07-27 00:00:01"), "Exponential Phase", Stage),
         Stage = if_else(datetime > as_datetime("2021-07-27 00:00:01") & datetime <= as_datetime("2021-08-16 00:00:01"), "Peak Growth", Stage),
         Stage = if_else(datetime > as_datetime("2021-08-16 00:00:01") & datetime <= as_datetime("2021-08-27 00:00:01"), "Bloom Collapse ", Stage),
         Stage = if_else(datetime > as_datetime("2021-08-27 00:00:01"), "Post-Bloom", Stage)) 

shapiro.test(SA_O2_Stage$ODOmgL)

test <- kruskal.test(ODOmgL~Stage, data=SA_O2_Stage)

library(dunn.test)

dunn.test(SA_O2_Stage$ODOmgL, SA_O2_Stage$Stage, method="bonferroni")


SA_O2_Stage %>%  
  group_by(Stage) %>%
  summarise(Avg = mean(ODOmgL),
            sd = sd(ODOmgL),
            max = max(ODOmgL),
            min = min(ODOmgL))
  
  

```
### Nutrients

# Phosphorus

```{r}
SA_P_Stats_S <- SA_P %>%
  mutate(Site = "SA") %>%
  filter(Location == "Water TP - 0.5m")

MB_P_Stats_S <- MB_P %>%
  mutate(Site = "MB") %>%
  filter(Location == "Water TP - 0.5m")


P_Stats_S <- rbind(SA_P_Stats_S, MB_P_Stats_S) %>%
  na.omit()

# Paired Samples Wilcoxon Test
result = t.test(TP_ugL ~ Site,
                    data = P_Stats_S,
                    paired = FALSE,
                    alternative = "two.sided")

# Printing the results
print(result)

P_Stats_S %>%
  group_by(Site) %>%
  summarise(Avg = mean(TP_ugL),
            sd = sd(TP_ugL),
            max = max(TP_ugL))



SA_P_Stats_B <- SA_P %>%
  mutate(Site = "SA") %>%
  filter(Location == "Water TP - 4.5m")

MB_P_Stats_B <- MB_P %>%
  mutate(Site = "MB") %>%
  filter(Location == "Water TP - 2.5m")


P_Stats_B <- rbind(SA_P_Stats_B, MB_P_Stats_B) %>%
  na.omit()

# Paired Samples Wilcoxon Test
result = t.test(TP_ugL ~ Site,
                    data = P_Stats_B,
                    paired = FALSE,
                    alternative = "two.sided")

# Printing the results
print(result)

P_Stats_B %>%
  group_by(Site) %>%
  summarise(Avg = mean(TP_ugL),
            sd = sd(TP_ugL),
            max = max(TP_ugL))

#####

SA_P_Stats_I <- SA_P %>%
  mutate(Site = "SA") %>%
  filter(Location == "Seston TP - IWC")

MB_P_Stats_I <- MB_P %>%
  mutate(Site = "MB") %>%
  filter(Location == "Seston TP - IWC")


P_Stats_I <- rbind(SA_P_Stats_I, MB_P_Stats_I) %>%
  na.omit()

# Paired Samples Wilcoxon Test
result = t.test(TP_ugL ~ Site,
                    data = P_Stats_I,
                    paired = FALSE,
                    alternative = "two.sided")

# Printing the results
print(result)

P_Stats_I %>%
  group_by(Site) %>%
  summarise(Avg = mean(TP_ugL),
            sd = sd(TP_ugL),
            max = max(TP_ugL))
```
# Nitrogen

```{r}
SA_N_Stats_S <- SA_N %>%
  mutate(Site = "SA") %>%
  filter(Location == "Water TN - 0.5m")

MB_N_Stats_S <- MB_N %>%
  mutate(Site = "MB") %>%
  filter(Location == "Water TN - 0.5m")


N_Stats_S <- rbind(SA_N_Stats_S, MB_N_Stats_S) %>%
  na.omit()

# Paired Samples Wilcoxon Test
result = t.test(TN_mgL ~ Site,
                    data = N_Stats_S,
                    paired = FALSE,
                    alternative = "two.sided")

# Printing the results
print(result)

N_Stats_S %>%
  group_by(Site) %>%
  summarise(Avg = mean(TN_mgL),
            sd = sd(TN_mgL),
            max = max(TN_mgL))



SA_N_Stats_B <- SA_N %>%
  mutate(Site = "SA") %>%
  filter(Location == "Water TN - 4.5m")

MB_N_Stats_B <- MB_N %>%
  mutate(Site = "MB") %>%
  filter(Location == "Water TN - 2.5m")


N_Stats_B <- rbind(SA_N_Stats_B, MB_N_Stats_B) %>%
  na.omit()

# Paired Samples Wilcoxon Test
result = t.test(TN_mgL ~ Site,
                    data = N_Stats_B,
                    paired = FALSE,
                    alternative = "two.sided")

# Printing the results
print(result)

N_Stats_B %>%
  group_by(Site) %>%
  summarise(Avg = mean(TN_mgL),
            sd = sd(TN_mgL),
            max = max(TN_mgL))

#####

SA_N_Stats_I <- SA_N %>%
  mutate(Site = "SA") %>%
  filter(Location == "Seston TN - IWC")

MB_N_Stats_I <- MB_N %>%
  mutate(Site = "MB") %>%
  filter(Location == "Seston TN - IWC")


N_Stats_I <- rbind(SA_N_Stats_I, MB_N_Stats_I) %>%
  na.omit()

# Paired Samples Wilcoxon Test
result = t.test(TN_mgL ~ Site,
                    data = N_Stats_I,
                    paired = FALSE,
                    alternative = "two.sided")

# Printing the results
print(result)

N_Stats_I %>%
  group_by(Site) %>%
  summarise(Avg = mean(TN_mgL),
            sd = sd(TN_mgL),
            max = max(TN_mgL))

#####

SA_DN_Stats_I <- SA_N %>%
  mutate(Site = "SA") %>%
  filter(Location == "Water TDN - IWC")

MB_DN_Stats_I <- MB_N %>%
  mutate(Site = "MB") %>%
  filter(Location == "Water TDN - IWC")


DN_Stats_I <- rbind(SA_DN_Stats_I, MB_DN_Stats_I) %>%
  na.omit()

# Paired Samples Wilcoxon Test
result = t.test(TN_mgL ~ Site,
                    data = DN_Stats_I,
                    paired = FALSE,
                    alternative = "two.sided")

# Printing the results
print(result)

DN_Stats_I %>%
  group_by(Site) %>%
  summarise(Avg = mean(TN_mgL),
            sd = sd(TN_mgL),
            max = max(TN_mgL))
```

# Carbon

```{r}
SA_C_Stats <- SA_C %>%
  mutate(Site = "SA") %>%
  filter(Location == "Water DOC - IWC")

MB_C_Stats <- MB_C %>%
  mutate(Site = "MB") %>%
  filter(Location == "Water DOC - IWC")



C_Stats <- rbind(SA_C_Stats, MB_C_Stats) %>%
  na.omit()

# Paired Samples Wilcoxon Test
result = t.test(C_mgL ~ Site,
                    data = C_Stats,
                    paired = FALSE,
                    alternative = "two.sided")

# Printing the results
print(result)

C_Stats %>%
  group_by(Site) %>%
  summarise(Avg = mean(C_mgL),
            sd = sd(C_mgL),
            max = max(C_mgL))



SA_C_Stats_S <- SA_C %>%
  mutate(Site = "SA") %>%
  filter(Location == "Seston C - IWC")

MB_C_Stats_S <- MB_C %>%
  mutate(Site = "MB") %>%
  filter(Location == "Seston C - IWC")



C_Stats_S <- rbind(SA_C_Stats_S, MB_C_Stats_S) %>%
  na.omit()

# Paired Samples Wilcoxon Test
result = t.test(C_mgL ~ Site,
                    data = C_Stats_S,
                    paired = FALSE,
                    alternative = "two.sided")

# Printing the results
print(result)

C_Stats_S %>%
  group_by(Site) %>%
  summarise(Avg = mean(C_mgL),
            sd = sd(C_mgL),
            max = max(C_mgL))


```

## Dissolved Nutrient Statistics

I need to add some statistics into the results section to compare the pre-bloom levels of DIN and PO4 between the bays to support my claim that the dissolved organic nitrogen is the important metric in determining bloom severity between these two systems. 

```{r}

DissNut_Stat <- DissNut %>%
  group_by(date, site) %>%
  summarise(DIN = mean(DIN),
            PO4 = mean(PO4)) %>%
  mutate(Stage = if_else(date <= as_date("2021-07-15") & site == "STA Inner", "Pre-Bloom", "None"),
         Stage = if_else(date > as_date("2021-07-15") & date <= as_date("2021-07-27") & site == "STA Inner", "Exponential Phase", Stage),
         Stage = if_else(date > as_date("2021-07-27") & date <= as_date("2021-08-16") & site == "STA Inner", "Peak Growth", Stage),
         Stage = if_else(date > as_date("2021-08-16") & date <= as_date("2021-08-27") & site == "STA Inner", "Bloom Collapse ", Stage),
         Stage = if_else(date > as_date("2021-08-27") & site == "STA Inner", "Post-Bloom", Stage)) %>%
  mutate(Stage = if_else(date <= as_date("2021-08-07") & site == "Miss Bay", "Pre-Bloom", Stage),
         Stage = if_else(date > as_date("2021-08-07") & date <= as_date("2021-08-12") & site == "Miss Bay", "Exponential Phase 1", Stage),
         Stage = if_else(date > as_date("2021-08-12") & date <= as_date("2021-08-20") & site == "Miss Bay", "Peak Growth 1", Stage),
         Stage = if_else(date > as_date("2021-08-20") & date <= as_date("2021-08-24") & site == "Miss Bay", "Bloom Collapse 1", Stage),
         Stage = if_else(date > as_date("2021-08-24") & date <= as_date("2021-09-03") & site == "Miss Bay", "Exponential Phase 2", Stage),
         Stage = if_else(date > as_date("2021-09-03") & date <= as_date("2021-09-15") & site == "Miss Bay", "Peak Growth 2", Stage),
         Stage = if_else(date > as_date("2021-09-15") & date <= as_date("2021-09-27") & site == "Miss Bay", "Bloom Collapse 2", Stage),
         Stage = if_else(date > as_date("2021-09-27") & site == "Miss Bay", "Post-Bloom", Stage)) 



DissNut_Stat%>%  
  group_by(Stage, site) %>%
  summarise(Avg = mean(DIN),
            sd = sd(DIN),
            max = max(DIN))


DissNut_Stat%>%  
  group_by(Stage, site) %>%
  summarise(Avg = mean(PO4),
            sd = sd(PO4),
            max = max(PO4))


## 6/20-6/23 Dissolved nutrient data: 


```

##### Toxin T - Tests

```{r}

Anatoxin_summ <- Toxins %>%
  filter(Anatoxin > 0) %>%
  group_by(Station) %>%
  summarize(avg_ana = mean(Anatoxin),
            se_ana = std.error(Anatoxin),
            n_ana = n())


Microcystin_summ <- Toxins %>%
  filter(Microcystin > 0) %>%
  group_by(Station) %>%
  summarize(avg_mc = mean(Microcystin),
            se_mc = std.error(Microcystin),
            n_mc = n())


## Toxins T-test

Toxins %>%
  filter(Station == "MB") %>%
  ggplot(aes(x=Microcystin))+
  geom_histogram()

Toxins %>%
  filter(Microcystin > 0) %>%
  ggplot(aes(x=Station, y=Microcystin, fill=Station, group=Station))+
  geom_boxplot()

Toxins %>%
  filter(Anatoxin > 0) %>%
  ggplot(aes(x=Station, y=Anatoxin, fill=Station, group=Station))+
  geom_boxplot()

### Two Sample T-Test
MC_TTest <- Toxins %>%
  filter(Microcystin > 0)

ATX_TTest <- Toxins %>%
  filter(Anatoxin > 0)

t.test(Microcystin ~ Station, data=MC_TTest)

t.test(Anatoxin ~ Station, data=ATX_TTest)



# Independent T-Test

SA_Toxins <- Toxins %>%
  filter(Station == "SA") %>%
  pivot_longer(cols=c(Microcystin, Anatoxin), names_to="Toxin", 
               values_to = "Concentration") %>%
  filter(Concentration > 0)

MB_Toxins <- Toxins %>%
  filter(Station == "MB") %>%
  pivot_longer(cols=c(Microcystin, Anatoxin), names_to="Toxin", 
               values_to = "Concentration") %>%
  filter(Concentration > 0)

t.test(Concentration ~ Toxin, data=MB_Toxins)

```

